---
title: "Abundance Analyses - Herbivore and Detritivore Insects"
author: "Rodolfo Pelinson"
date: "26/12/2022"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = TRUE, message=FALSE, warning=FALSE}
library(glmmTMB)
library(car)
library(emmeans)
library(DHARMa)
library(AICcmodavg)

```


Before anything, lets load and prepare some data sheets and vectors for the analysis.
```{r include = FALSE}
setwd("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/IsolationAgrochemicals")
source("Auxiliary scripts/Loading_data.R")
```


# Herbivore and Detritivore Insects

First, lets make vectors of the abundances (summing up the abundance of all herbivore and detritivore insects in each sample):

```{r, warning=FALSE}
#cheking if the order of row in Trait_og and columns in com_orig match
data.frame(com = colnames(com_orig), trait = Trait_orig$genus)

com_herb_det_ab <- rowSums(com_orig[,which(Trait_orig$trait == "insect_consumer")])

com_herb_det_ab_SS1 <- com_herb_det_ab[SS == "1"]
com_herb_det_ab_SS2 <- com_herb_det_ab[SS == "2"]
com_herb_det_ab_SS3 <- com_herb_det_ab[SS == "3"]
com_herb_det_ab_SS4 <- com_herb_det_ab[SS == "4"]
```

## All surveys


First, lets see what is the best probability distribution to model the data

```{r, dpi=150, fig.width=3, fig.height=3, fig.align = 'center', warning=FALSE}
par(cex = 0.6)

data <- data.frame(ID = ID,
                         treatments = treatments_all,
                         isolation = isolation_all,
                         survey = SS,
                         survey_12_3_4 = SS_12_3_4,
                         survey_1_2_34 = SS_1_2_34,
                         survey_1_23_4 = SS_1_23_4,
                         survey_123_4 = SS_123_4,
                         survey_1_234 = SS_1_234)
#Gaussian
mod_herb_det_G <- glmmTMB(com_herb_det_ab ~ isolation * treatments * survey  + (1|ID), family = "gaussian", data = data)
simulationResiduals_mod_herb_det_G <- simulateResiduals(fittedModel = mod_herb_det_G, plot = F, seed = 3, n = 1000)
plotQQunif(simulationResiduals_mod_herb_det_G, testUniformity = F, testOutliers = F, testDispersion = F, cex.lab = 1.5, cex.main = 1.5) 
plotResiduals(simulationResiduals_mod_herb_det_G,  quantreg = F, cex.lab = 1.5, cex.main = 1.5)

#Poisson
mod_herb_det_P <- glmmTMB(com_herb_det_ab ~ isolation * treatments * survey  + (1|ID), family = "poisson", data = data)
simulationResiduals_mod_herb_det_P <- simulateResiduals(fittedModel = mod_herb_det_P, plot = F, seed = 3, n = 1000)
plotQQunif(simulationResiduals_mod_herb_det_P, testUniformity = F, testOutliers = F, testDispersion = F, cex.lab = 1.5, cex.main = 1.5) 
plotResiduals(simulationResiduals_mod_herb_det_P,  quantreg = F, cex.lab = 1.5, cex.main = 1.5)

#Negative Binomial
mod_herb_det_NB <- glmmTMB(com_herb_det_ab ~ isolation * treatments * survey  + (1|ID), family = nbinom2(link = "log"), data = data)
simulationResiduals_mod_herb_det_NB <- simulateResiduals(fittedModel = mod_herb_det_NB, plot = F, seed = 3, n = 1000)
plotQQunif(simulationResiduals_mod_herb_det_NB, testUniformity = F, testOutliers = F, testDispersion = F, cex.lab = 1.5, cex.main = 1.5) 
plotResiduals(simulationResiduals_mod_herb_det_NB,  quantreg = F, cex.lab = 1.5, cex.main = 1.5)

AIC(mod_herb_det_G, mod_herb_det_P, mod_herb_det_NB)
```
It looks like the negative binomial distribution is the one to be chosen.

Now the analysis
```{r, warning=FALSE}
mod_herb_det_no_effect <- glmmTMB(com_herb_det_ab ~ 1 + (1|ID), family = nbinom2(link = "log"), data = data)
mod_herb_det_survey <- glmmTMB(com_herb_det_ab ~ survey+ (1|ID), family = nbinom2(link = "log"), data = data)
mod_herb_det_treatments <- glmmTMB(com_herb_det_ab ~ isolation * treatments+ (1|ID), family = nbinom2(link = "log"), data = data)
mod_herb_det_survey_treatments <- glmmTMB(com_herb_det_ab ~ survey + (isolation * treatments)+ (1|ID), family = nbinom2(link = "log"), data = data)
mod_herb_det_survey_i_treatments <- glmmTMB(com_herb_det_ab ~ survey * (isolation * treatments)+ (1|ID), family = nbinom2(link = "log"), data = data)

model_selection_herb_det <- aictab(list(mod_herb_det_no_effect,
                                        mod_herb_det_survey,
                                        mod_herb_det_treatments,
                                        mod_herb_det_survey_treatments,
                                        mod_herb_det_survey_i_treatments),
                                        modnames = c("No Effect",
                                                     "Survey",
                                                     "Treatments",
                                                     "Survey + Treatments",
                                                     "Survey * Treatments"), sort = FALSE)

model_selection_herb_det
```
It seems that the an additive effect of treatments and survey are equally plausible.

Lets see of all surveys are different
```{r}
mod_herb_det_survey_1_2_3_4 <- glmmTMB(com_herb_det_ab ~ survey * (isolation * treatments) + (1|ID), family = nbinom2(link = "log"), data = data)
mod_herb_det_survey_12_3_4 <- glmmTMB(com_herb_det_ab ~ survey_12_3_4 * (isolation * treatments) + (1|ID), family = nbinom2(link = "log"), data = data)
mod_herb_det_survey_1_2_34 <- glmmTMB(com_herb_det_ab ~ survey_1_2_34 * (isolation * treatments) + (1|ID), family = nbinom2(link = "log"), data = data)
mod_herb_det_survey_1_23_4 <- glmmTMB(com_herb_det_ab ~ survey_1_23_4 * (isolation * treatments) + (1|ID), family = nbinom2(link = "log"), data = data)
mod_herb_det_survey_123_4 <- glmmTMB(com_herb_det_ab ~ survey_123_4 * (isolation * treatments) + (1|ID), family = nbinom2(link = "log"), data = data)
mod_herb_det_survey_1_234 <- glmmTMB(com_herb_det_ab ~ survey_1_234 * (isolation * treatments) + (1|ID), family = nbinom2(link = "log"), data = data)

model_selection_herb_det_survey <- aictab(list(mod_herb_det_survey_1_2_3_4,
                                        mod_herb_det_survey_12_3_4,
                                        mod_herb_det_survey_1_2_34,
                                        mod_herb_det_survey_1_23_4,
                                        mod_herb_det_survey_123_4,
                                        mod_herb_det_survey_1_234),
                                        modnames = c("1 # 2 # 3 # 4",
                                                              "(1 = 2) # 3 # 4",
                                                              "1 # 2 # (3 = 4)",
                                                              "1 # (2 = 3) # 4",
                                                              "(1 = 2 = 3) # 4",
                                                              "1 # (2 = 3 = 4)"), sort = FALSE)

model_selection_herb_det_survey
```
It looks like all surveys are different.

Ploting it:
```{r, dpi=150, fig.width=3, fig.height=3, fig.align = 'center', warning=FALSE}
col_survey_1 <- "#0072B2"
col_survey_2 <- "#CC79A7"
col_survey_3 <- "#D55E00"
col_survey_4 <- "#E69F00"

par(mar = c(3.5, 4, 0.1, 0.1)+ 0.1, cex = 0.7, bty = "l")
boxplot(com_herb_det_ab ~ SS, outline = T,
        ylab = "", xlab = "", at = c(1,2,4,8), lwd = 0.5,
        main = "", xaxt="n", yaxt = "n", range = 1.5,
        col = rep(c(col_survey_1, col_survey_2, col_survey_3, col_survey_4),3), lty = 1,
        pch = 21, bg = rep(c(col_survey_1, col_survey_2, col_survey_3, col_survey_4),3), cex = 1)
        #ylim = c(0,140))

title(ylab="Total Abundance", line=2.5, cex.lab=1.52)
#title(main= "Predatory Insects", adj = 1)
axis(2, cex.axis = 1, gap.axis = -1)
axis(1,labels = c("20","40","80", "160"), cex.axis = 1.25, at =c(1,2,4,8), line = 0, tick = F, gap.axis = -1)
title(xlab="Time (days)", line=2.5, cex.lab=1.52)
axis(1,labels = rep("",4), cex.axis = 0.8, at =c(1,2,4,8), line = 0,tick = T)
```

## First Survey (20 day)
```{r, warning=FALSE}
data_SS1 <- data.frame(isolation = isolation_SS1, treatments = treatments_SS1, isolation30120_480, isolation30120_480)


mod_herb_det_SS1_no_effect <- glmmTMB(com_herb_det_ab_SS1 ~ 1, family = nbinom2(link = "log"), data = data_SS1)
mod_herb_det_SS1_treatments <- glmmTMB(com_herb_det_ab_SS1 ~ treatments, family = nbinom2(link = "log"), data = data_SS1)
mod_herb_det_SS1_isolation <- glmmTMB(com_herb_det_ab_SS1 ~ isolation, family = nbinom2(link = "log"), data = data_SS1)
mod_herb_det_SS1_isolation_treatments <- glmmTMB(com_herb_det_ab_SS1 ~ isolation + treatments, family = nbinom2(link = "log"), data = data_SS1)
mod_herb_det_SS1_isolation_i_treatments <- glmmTMB(com_herb_det_ab_SS1 ~ isolation * treatments, family = nbinom2(link = "log"), data = data_SS1)

model_selection_herb_det_SS1 <- aictab(list(mod_herb_det_SS1_no_effect,
                                             mod_herb_det_SS1_treatments,
                                             mod_herb_det_SS1_isolation,
                                             mod_herb_det_SS1_isolation_treatments,
                                             mod_herb_det_SS1_isolation_i_treatments),
                                        modnames = c("No Effect",
                                                     "Treatments",
                                                     "Isolation",
                                                     "Treatments + Isolation",
                                                     "Treatments * Isolation"), sort = FALSE)

model_selection_herb_det_SS1
```
There is an important effect of isolation, lets see which levels are different from which.

```{r, warning=FALSE}
mod_herb_det_SS1_30120_480 <- glmmTMB(com_herb_det_ab_SS1 ~ isolation30120_480, family = nbinom2(link = "log"), data = data_SS1)
mod_herb_det_SS1_30_120480 <- glmmTMB(com_herb_det_ab_SS1 ~ isolation30_120480, family = nbinom2(link = "log"), data = data_SS1)

model_selection_herb_det_SS1_post_hoc_isolation <- aictab(list(mod_herb_det_SS1_isolation,
                                                                mod_herb_det_SS1_30120_480,
                                                                mod_herb_det_SS1_30_120480),
                                                           modnames = c("30 # 120 # 480",
                                                                        "(30 = 120) # 480",
                                                                        "30 # (120 = 480)"), sort = FALSE)

model_selection_herb_det_SS1_post_hoc_isolation

```
It appears that 30m is different from 120m and 480m.


Ploting it:
```{r, dpi=150, fig.width=3, fig.height=3, fig.align = 'center', warning=FALSE}
col_sugarcane <- "#CC6677"
col_pasture <- "#DDCC77"
col_control <- "#88CCEE"

par(mar = c(3.5, 4, 0.1, 0.1)+ 0.1, cex = 0.7, bty = "l")
boxplot(com_herb_det_ab_SS1 ~ treatments_SS1*isolation_SS1, outline = T,
        ylab = "", xlab = "", at = c(1,2,3, 5,6,7, 9,10,11), lwd = 0.5,
        main = "", xaxt="n", yaxt = "n", range = 1.5,
        col = rep(c(col_control, col_pasture, col_sugarcane),3), lty = 1,
        pch = 21, bg = rep(c(col_control, col_pasture, col_sugarcane),3), cex = 1,
ylim = c(0,150))

title(ylab="Total Abundance", line=2.5, cex.lab=1.52)
#title(main= "Predatory Insects", adj = 1)
axis(2, cex.axis = 1, gap.axis = -1)
axis(1,labels = c("30 m","120 m","480 m"), cex.axis = 1.25, at =c(2,6,10), line = 0.5, tick = F, gap.axis = -1)
axis(1,labels = rep("",9), cex.axis = 0.8, at =c(1,2,3, 5,6,7, 9,10,11), line = 0,tick = T)


position1 <- 150
text(y = rep(position1, 3),x = c(2, 6, 10),
     labels = c("b","a","a"),
     cex = 1, adj = c(0.5,0.5),
     col = c("grey0","grey50","grey50"))

arrows(x0 = c(1, 5, 9) - 0.4,
       y0 = rep(position1*0.95, 9),
       x1 = c(3, 7, 11) + 0.4,
       y1 = rep(position1*0.95, 9),
       code = 0, col = c("grey0","grey50","grey50"))

legend(x = 7, y = 100, fill = c(col_control, col_pasture, col_sugarcane), legend = c("Control", "Pasture", "Sugarcane"), cex = 1)



```


## Second Survey (40 day)

Now the analysis
```{r, warning=FALSE}
data_SS2 <- data.frame(ID = ID_SS2_3_4, isolation = isolation_SS2_3_4, treatments = treatments_SS2_3_4,
                       treatments_contpast_sug = treatments_SS2_3_4_contpast_sug,
                       treatments_cont_pastsug = treatments_SS2_3_4_cont_pastsug,
                       treatments_contsug_past = treatments_SS2_3_4_contsug_past,
                       isolation30120_480 = isolation30120_480_SS2_3_4,
                       isolation30_120480 = isolation30_120480_SS2_3_4)


mod_herb_det_SS2_no_effect <- glmmTMB(com_herb_det_ab_SS2 ~ 1 + (1|ID), family = nbinom2(link = "log"), data = data_SS2)
mod_herb_det_SS2_isolation <- glmmTMB(com_herb_det_ab_SS2 ~ isolation + (1|ID), family = nbinom2(link = "log"), data = data_SS2)
mod_herb_det_SS2_treatments <- glmmTMB(com_herb_det_ab_SS2 ~ treatments + (1|ID), family = nbinom2(link = "log"), data = data_SS2)
mod_herb_det_SS2_treatments_isolation <- glmmTMB(com_herb_det_ab_SS2 ~ treatments + isolation + (1|ID), family = nbinom2(link = "log"), data = data_SS2)
mod_herb_det_SS2_treatments_i_isolation <- glmmTMB(com_herb_det_ab_SS2 ~ treatments * isolation + (1|ID), family = nbinom2(link = "log"), data = data_SS2)



model_selection_herb_det_SS2 <- aictab(list(mod_herb_det_SS2_no_effect,
                                             mod_herb_det_SS2_treatments,
                                             mod_herb_det_SS2_isolation,
                                             mod_herb_det_SS2_treatments_isolation,
                                             mod_herb_det_SS2_treatments_i_isolation),
                                        modnames = c("No Effect",
                                                     "Treatments",
                                                     "Isolation",
                                                     "Treatments + Isolation",
                                                     "Treatments * Isolation"), sort = FALSE)

model_selection_herb_det_SS2


```

Ok. There are important effects of treatments and isolation. The model that includes an interaction between the two was also plausible, but not as much. In this case, it is parcimonious to stick with the model that only contains main effects.

```{r, warning=FALSE}
mod_herb_det_SS2_contpast_sug <- glmmTMB(com_herb_det_ab_SS2 ~ isolation + treatments_contpast_sug + (1|ID), family = nbinom2(link = "log"), data = data_SS2)
mod_herb_det_SS2_cont_pastsug <- glmmTMB(com_herb_det_ab_SS2 ~ isolation + treatments_cont_pastsug + (1|ID), family = nbinom2(link = "log"), data = data_SS2)
mod_herb_det_SS2_contsug_past <- glmmTMB(com_herb_det_ab_SS2 ~ isolation + treatments_contsug_past + (1|ID), family = nbinom2(link = "log"), data = data_SS2)

model_selection_herb_det_SS2_post_hoc_treatments <- aictab(list(mod_herb_det_SS2_treatments_isolation,
                                                                 mod_herb_det_SS2_contpast_sug,
                                                                 mod_herb_det_SS2_cont_pastsug,
                                                                 mod_herb_det_SS2_contsug_past),
                                                            modnames = c("Control # Pasture # Sugarcane",
                                                                         "(Control = Pasture) # Sugarcane",
                                                                         "Control # (Pasture = Sugarcane)",
                                                                         "(Control = Sugarcane) # Pasture"), sort = FALSE)


model_selection_herb_det_SS2_post_hoc_treatments
```
It looks like we only have enough evidence to say that the sugarcane treatment is different from the others.


```{r, warning=FALSE}
mod_herb_det_SS2_30120_480 <- glmmTMB(com_herb_det_ab_SS2 ~ treatments + isolation30120_480 + (1|ID), family = nbinom2(link = "log"), data = data_SS2)
mod_herb_det_SS2_30_120480 <- glmmTMB(com_herb_det_ab_SS2 ~ treatments + isolation30_120480 + (1|ID), family = nbinom2(link = "log"), data = data_SS2)

model_selection_herb_det_SS2_post_hoc_isolation <- aictab(list(mod_herb_det_SS2_treatments_isolation,
                                                               mod_herb_det_SS2_30120_480,
                                                               mod_herb_det_SS2_30_120480),
                                                          modnames = c("30 # 120 # 480",
                                                                       "(30 = 120) # 480",
                                                                       "30 # (120 = 480)"), sort = FALSE)

model_selection_herb_det_SS2_post_hoc_isolation

```
It looks like we only have enough evidence to say that the 480m of isolation is different from the 30m.


```{r, dpi=150, fig.width=3, fig.height=3, fig.align = 'center', warning=FALSE}
par(mar = c(3.5, 4, 0.1, 0.1)+ 0.1, cex = 0.7, bty = "l")
boxplot(com_herb_det_ab_SS2 ~ treatments_SS2_3_4*isolation_SS2_3_4, outline = T,
        ylab = "", xlab = "", at = c(1,2,3, 5,6,7, 9,10,11), lwd = 0.5,
        main = "", xaxt="n", yaxt = "n", range = 1.5,
        col = rep(c(col_control, col_pasture, col_sugarcane),3), lty = 1,
        pch = 21, bg = rep(c(col_control, col_pasture, col_sugarcane),3), cex = 1,
        ylim = c(0,230))

title(ylab="Total Abundance", line=2.5, cex.lab=1.52)
#title(main= "Predatory Insects", adj = 1)
axis(2, cex.axis = 1, gap.axis = -1)
axis(1,labels = c("30 m","120 m","480 m"), cex.axis = 1.25, at =c(2,6,10), line = 0.5, tick = F, gap.axis = -1)
axis(1,labels = rep("",9), cex.axis = 0.8, at =c(1,2,3, 5,6,7, 9,10,11), line = 0,tick = T)


position1 <- 230
text(y = rep(position1, 3),x = c(2, 6, 10),
     labels = c("a","ab","b"),
     cex = 1, adj = c(0.5,0.5),
     col = c("grey50","grey25","grey0"))

arrows(x0 = c(1, 5, 9) - 0.4,
       y0 = rep(position1*0.95, 9),
       x1 = c(3, 7, 11) + 0.4,
       y1 = rep(position1*0.95, 9),
       code = 0, col = c("grey50","grey25","grey0"))



position2 <- position1 * 0.9

text(y = rep(position2, 9),x = c(1,2,3, 5,6,7, 9,10,11),
     labels = c("b","b","a",   "b","b","a",   "b","b","a"),
     cex = 1, adj = c(0.5,0.5),
     col = c("grey0","grey0","grey50",   "grey0","grey0","grey50",   "grey0","grey0","grey50"))

arrows(x0 = c(1, 2,3, 5, 6,7, 9,10,11) - 0.4,
       y0 = rep(position2*0.95, 9),
       x1 = c(1, 2,3, 5, 6,7, 9,10,11) + 0.4,
       y1 = rep(position2*0.95, 9),
       code = 0, col = c("grey0","grey0","grey50",   "grey0","grey0","grey50",   "grey0","grey0","grey50"))


```



## Third Survey (80 day)

```{r, warning=FALSE}
data_SS3 <- data.frame(ID = ID_SS2_3_4, isolation = isolation_SS2_3_4, treatments = treatments_SS2_3_4,
                       treatments_contpast_sug = treatments_SS2_3_4_contpast_sug,
                       treatments_cont_pastsug = treatments_SS2_3_4_cont_pastsug,
                       treatments_contsug_past = treatments_SS2_3_4_contsug_past,
                       isolation30120_480 = isolation30120_480_SS2_3_4,
                       isolation30_120480 = isolation30_120480_SS2_3_4)


mod_herb_det_SS3_no_effect <- glmmTMB(com_herb_det_ab_SS3 ~ 1 + (1|ID), family = nbinom2(link = "log"), data = data_SS3)
mod_herb_det_SS3_isolation <- glmmTMB(com_herb_det_ab_SS3 ~ isolation + (1|ID), family = nbinom2(link = "log"), data = data_SS3)
mod_herb_det_SS3_treatments <- glmmTMB(com_herb_det_ab_SS3 ~ treatments + (1|ID), family = nbinom2(link = "log"), data = data_SS3)
mod_herb_det_SS3_treatments_isolation <- glmmTMB(com_herb_det_ab_SS3 ~ treatments + isolation + (1|ID), family = nbinom2(link = "log"), data = data_SS3)
mod_herb_det_SS3_treatments_i_isolation <- glmmTMB(com_herb_det_ab_SS3 ~ treatments * isolation + (1|ID), family = nbinom2(link = "log"), data = data_SS3)



model_selection_herb_det_SS3 <- aictab(list(mod_herb_det_SS3_no_effect,
                                             mod_herb_det_SS3_treatments,
                                             mod_herb_det_SS3_isolation,
                                             mod_herb_det_SS3_treatments_isolation,
                                             mod_herb_det_SS3_treatments_i_isolation),
                                        modnames = c("No Effect",
                                                     "Treatments",
                                                     "Isolation",
                                                     "Treatments + Isolation",
                                                     "Treatments * Isolation"), sort = FALSE)

model_selection_herb_det_SS3

```

Again, important main effects of isolation and agrochemical treatments.

```{r, warning=FALSE}

mod_herb_det_SS3_contpast_sug <- glmmTMB(com_herb_det_ab_SS3 ~ isolation + treatments_contpast_sug + (1|ID), family = nbinom2(link = "log"), data = data_SS3)
mod_herb_det_SS3_cont_pastsug <- glmmTMB(com_herb_det_ab_SS3 ~ isolation + treatments_cont_pastsug + (1|ID), family = nbinom2(link = "log"), data = data_SS3)
mod_herb_det_SS3_contsug_past <- glmmTMB(com_herb_det_ab_SS3 ~ isolation + treatments_contsug_past + (1|ID), family = nbinom2(link = "log"), data = data_SS3)

model_selection_herb_det_SS3_post_hoc_treatments <- aictab(list(mod_herb_det_SS3_treatments_isolation,
                                                                mod_herb_det_SS3_contpast_sug,
                                                                mod_herb_det_SS3_cont_pastsug,
                                                                mod_herb_det_SS3_contsug_past),
                                                           modnames = c("Control # Pasture # Sugarcane",
                                                                        "(Control = Pasture) # Sugarcane",
                                                                        "Control # (Pasture = Sugarcane)",
                                                                        "(Control = Sugarcane) # Pasture"), sort = FALSE)

model_selection_herb_det_SS3_post_hoc_treatments


```
It looks like Pasture is actually different from both control and sugarcane!


```{r, warning=FALSE}
mod_herb_det_SS3_30120_480 <- glmmTMB(com_herb_det_ab_SS3 ~ treatments + isolation30120_480 + (1|ID), family = nbinom2(link = "log"), data = data_SS3)
mod_herb_det_SS3_30_120480 <- glmmTMB(com_herb_det_ab_SS3 ~ treatments + isolation30_120480 + (1|ID), family = nbinom2(link = "log"), data = data_SS3)

model_selection_herb_det_SS3_post_hoc_isolation <- aictab(list(mod_herb_det_SS3_treatments_isolation,
                                                               mod_herb_det_SS3_30120_480,
                                                               mod_herb_det_SS3_30_120480),
                                                          modnames = c("30 # 120 # 480",
                                                                       "(30 = 120) # 480",
                                                                       "30 # (120 = 480)"), sort = FALSE)
model_selection_herb_det_SS3_post_hoc_isolation

```
For isolation , 480m is different from 30 and 120m.

Ploting it
```{r, dpi=150, fig.width=3, fig.height=3, fig.align = 'center', warning=FALSE}
par(mar = c(3.5, 4, 0.1, 0.1)+ 0.1, cex = 0.7, bty = "l")

boxplot(com_herb_det_ab_SS3 ~ treatments_SS2_3_4*isolation_SS2_3_4, outline = T,
        ylab = "", xlab = "", at = c(1,2,3, 5,6,7, 9,10,11), lwd = 0.5,
        main = "", xaxt="n", yaxt = "n", range = 1.5,
        col = rep(c(col_control, col_pasture, col_sugarcane),3), lty = 1,
        pch = 21, bg = rep(c(col_control, col_pasture, col_sugarcane),3), cex = 1,
        ylim = c(0,700))

title(ylab="Total Abundance", line=2.5, cex.lab=1.52)
#title(main= "Predatory Insects", adj = 1)
axis(2, cex.axis = 1, gap.axis = -1)
axis(1,labels = c("30 m","120 m","480 m"), cex.axis = 1.25, at =c(2,6,10), line = 0.5, tick = F, gap.axis = -1)
axis(1,labels = rep("",9), cex.axis = 0.8, at =c(1,2,3, 5,6,7, 9,10,11), line = 0,tick = T)

position1 <- 700
text(y = rep(position1, 3),x = c(2, 6, 10),
     labels = c("a","a","b"),
     cex = 1, adj = c(0.5,0.5),
     col = c("grey50","grey50","grey0"))

arrows(x0 = c(1, 5, 9) - 0.4,
       y0 = rep(position1*0.95, 9),
       x1 = c(3, 7, 11) + 0.4,
       y1 = rep(position1*0.95, 9),
       code = 0, col = c("grey50","grey50","grey0"))



position2 <- position1 * 0.9

text(y = rep(position2, 9),x = c(1,2,3, 5,6,7, 9,10,11),
     labels = c("a","b","a",   "a","b","a",   "a","b","a"),
     cex = 1, adj = c(0.5,0.5),
     col = c("grey50","grey0","grey50",   "grey50","grey0","grey50",   "grey50","grey0","grey50"))

arrows(x0 = c(1, 2,3, 5, 6,7, 9,10,11) - 0.4,
       y0 = rep(position2*0.95, 9),
       x1 = c(1, 2,3, 5, 6,7, 9,10,11) + 0.4,
       y1 = rep(position2*0.95, 9),
       code = 0, col = c("grey50","grey0","grey50",   "grey50","grey0","grey50",   "grey50","grey0","grey50"))


```




## Fourth Survey (160 day)
```{r, warning=FALSE}
data_SS4 <- data.frame(ID = ID_SS2_3_4, isolation = isolation_SS2_3_4, treatments = treatments_SS2_3_4,
                       treatments_contpast_sug = treatments_SS2_3_4_contpast_sug,
                       treatments_cont_pastsug = treatments_SS2_3_4_cont_pastsug,
                       treatments_contsug_past = treatments_SS2_3_4_contsug_past,
                       isolation30120_480 = isolation30120_480_SS2_3_4,
                       isolation30_120480 = isolation30_120480_SS2_3_4)


mod_herb_det_SS4_no_effect <- glmmTMB(com_herb_det_ab_SS4 ~ 1 + (1|ID), family = nbinom2(link = "log"), data = data_SS4)
mod_herb_det_SS4_isolation <- glmmTMB(com_herb_det_ab_SS4 ~ isolation + (1|ID), family = nbinom2(link = "log"), data = data_SS4)
mod_herb_det_SS4_treatments <- glmmTMB(com_herb_det_ab_SS4 ~ treatments + (1|ID), family = nbinom2(link = "log"), data = data_SS4)
mod_herb_det_SS4_treatments_isolation <- glmmTMB(com_herb_det_ab_SS4 ~ treatments + isolation + (1|ID), family = nbinom2(link = "log"), data = data_SS4)
mod_herb_det_SS4_treatments_i_isolation <- glmmTMB(com_herb_det_ab_SS4 ~ treatments * isolation + (1|ID), family = nbinom2(link = "log"), data = data_SS4)



model_selection_herb_det_SS4 <- aictab(list(mod_herb_det_SS4_no_effect,
                                            mod_herb_det_SS4_treatments,
                                            mod_herb_det_SS4_isolation,
                                            mod_herb_det_SS4_treatments_isolation,
                                            mod_herb_det_SS4_treatments_i_isolation),
                                       modnames = c("No Effect",
                                                    "Treatments",
                                                    "Isolation",
                                                    "Treatments + Isolation",
                                                    "Treatments * Isolation"), sort = FALSE)


model_selection_herb_det_SS4

```
There is an interaction between isolation and agrochemical treatments. Now we will make multiple comparisons of treatments in each isolation and of isolation in multiple treatments.

First, treatments
```{r, warning=FALSE}
#30
mod_herb_det_SS4_no_effect_30 <- glmmTMB(com_herb_det_ab_SS4[data_SS4$isolation == "30"] ~  1 + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$isolation == "30",])
mod_herb_det_SS4_treatments_30 <- glmmTMB(com_herb_det_ab_SS4[data_SS4$isolation == "30"] ~  treatments + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$isolation == "30",])
mod_herb_det_SS4_contpast_sug_30 <- glmmTMB(com_herb_det_ab_SS4[data_SS4$isolation == "30"] ~  treatments_contpast_sug + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$isolation == "30",])
mod_herb_det_SS4_cont_pastsug_30 <- glmmTMB(com_herb_det_ab_SS4[data_SS4$isolation == "30"] ~  treatments_cont_pastsug + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$isolation == "30",])
mod_herb_det_SS4_contsug_past_30 <- glmmTMB(com_herb_det_ab_SS4[data_SS4$isolation == "30"] ~  treatments_contsug_past + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$isolation == "30",])

model_selection_herb_det_SS4_post_hoc_treatments_30 <- aictab(list(mod_herb_det_SS4_no_effect_30,
                                                                   mod_herb_det_SS4_treatments_30,
                                                                   mod_herb_det_SS4_contpast_sug_30,
                                                                   mod_herb_det_SS4_cont_pastsug_30,
                                                                   mod_herb_det_SS4_contsug_past_30),
                                                           modnames = c("No Effect",
                                                             "Control # Pasture # Sugarcane",
                                                                        "(Control = Pasture) # Sugarcane",
                                                                        "Control # (Pasture = Sugarcane)",
                                                                        "(Control = Sugarcane) # Pasture"), sort = FALSE)


model_selection_herb_det_SS4_post_hoc_treatments_30


#120
mod_herb_det_SS4_no_effect_120 <- glmmTMB(com_herb_det_ab_SS4[data_SS4$isolation == "120"] ~  1 + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$isolation == "120",])
mod_herb_det_SS4_treatments_120 <- glmmTMB(com_herb_det_ab_SS4[data_SS4$isolation == "120"] ~  treatments + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$isolation == "120",])
mod_herb_det_SS4_contpast_sug_120 <- glmmTMB(com_herb_det_ab_SS4[data_SS4$isolation == "120"] ~  treatments_contpast_sug + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$isolation == "120",])
mod_herb_det_SS4_cont_pastsug_120 <- glmmTMB(com_herb_det_ab_SS4[data_SS4$isolation == "120"] ~  treatments_cont_pastsug + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$isolation == "120",])
mod_herb_det_SS4_contsug_past_120 <- glmmTMB(com_herb_det_ab_SS4[data_SS4$isolation == "120"] ~  treatments_contsug_past + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$isolation == "120",])

model_selection_herb_det_SS4_post_hoc_treatments_120 <- aictab(list(mod_herb_det_SS4_no_effect_120,
                                                                   mod_herb_det_SS4_treatments_120,
                                                                   mod_herb_det_SS4_contpast_sug_120,
                                                                   mod_herb_det_SS4_cont_pastsug_120,
                                                                   mod_herb_det_SS4_contsug_past_120),
                                                              modnames = c("No Effect",
                                                                           "Control # Pasture # Sugarcane",
                                                                           "(Control = Pasture) # Sugarcane",
                                                                           "Control # (Pasture = Sugarcane)",
                                                                           "(Control = Sugarcane) # Pasture"), sort = FALSE)


model_selection_herb_det_SS4_post_hoc_treatments_120


#480
mod_herb_det_SS4_no_effect_480 <- glmmTMB(com_herb_det_ab_SS4[data_SS4$isolation == "480"] ~  1 + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$isolation == "480",])
mod_herb_det_SS4_treatments_480 <- glmmTMB(com_herb_det_ab_SS4[data_SS4$isolation == "480"] ~  treatments + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$isolation == "480",])
mod_herb_det_SS4_contpast_sug_480 <- glmmTMB(com_herb_det_ab_SS4[data_SS4$isolation == "480"] ~  treatments_contpast_sug + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$isolation == "480",])
mod_herb_det_SS4_cont_pastsug_480 <- glmmTMB(com_herb_det_ab_SS4[data_SS4$isolation == "480"] ~  treatments_cont_pastsug + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$isolation == "480",])
mod_herb_det_SS4_contsug_past_480 <- glmmTMB(com_herb_det_ab_SS4[data_SS4$isolation == "480"] ~  treatments_contsug_past + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$isolation == "480",])

model_selection_herb_det_SS4_post_hoc_treatments_480 <- aictab(list(mod_herb_det_SS4_no_effect_480,
                                                                    mod_herb_det_SS4_treatments_480,
                                                                    mod_herb_det_SS4_contpast_sug_480,
                                                                    mod_herb_det_SS4_cont_pastsug_480,
                                                                    mod_herb_det_SS4_contsug_past_480),
                                                               modnames = c("No Effect",
                                                                            "Control # Pasture # Sugarcane",
                                                                            "(Control = Pasture) # Sugarcane",
                                                                            "Control # (Pasture = Sugarcane)",
                                                                            "(Control = Sugarcane) # Pasture"), sort = FALSE)


model_selection_herb_det_SS4_post_hoc_treatments_480
```

There is only an effect of treatments in the lowest isolation distance (30m), where pasture is different from control and sugarcane.

Now isolation

```{r, warning=FALSE}
#control
mod_herb_det_SS4_no_effect_control <- glmmTMB(com_herb_det_ab_SS4[data_SS4$treatments == "control"] ~  1 + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$treatments == "control",])
mod_herb_det_SS4_isolation_control <- glmmTMB(com_herb_det_ab_SS4[data_SS4$treatments == "control"] ~  isolation + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$treatments == "control",])
mod_herb_det_SS4_isolation30_120480_control  <- glmmTMB(com_herb_det_ab_SS4[data_SS4$treatments == "control"] ~  isolation30_120480 + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$treatments == "control",])
mod_herb_det_SS4_isolation30120_480_control  <- glmmTMB(com_herb_det_ab_SS4[data_SS4$treatments == "control"] ~  isolation30120_480 + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$treatments == "control",])

model_selection_herb_det_SS4_post_hoc_isolation_control <- aictab(list(mod_herb_det_SS4_no_effect_control,
                                                                        mod_herb_det_SS4_isolation_control,
                                                                        mod_herb_det_SS4_isolation30_120480_control,
                                                                        mod_herb_det_SS4_isolation30120_480_control),
                                                              modnames = c("No Effect",
                                                                           "30 # 120 # 480",
                                                                           "30 # (120 = 480)",
                                                                           "(30 = 120) # 480"), sort = FALSE)

model_selection_herb_det_SS4_post_hoc_isolation_control

#pasture
mod_herb_det_SS4_no_effect_pasture <- glmmTMB(com_herb_det_ab_SS4[data_SS4$treatments == "pasture"] ~  1 + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$treatments == "pasture",])
mod_herb_det_SS4_isolation_pasture <- glmmTMB(com_herb_det_ab_SS4[data_SS4$treatments == "pasture"] ~  isolation + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$treatments == "pasture",])
mod_herb_det_SS4_isolation30_120480_pasture  <- glmmTMB(com_herb_det_ab_SS4[data_SS4$treatments == "pasture"] ~  isolation30_120480 + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$treatments == "pasture",])
mod_herb_det_SS4_isolation30120_480_pasture  <- glmmTMB(com_herb_det_ab_SS4[data_SS4$treatments == "pasture"] ~  isolation30120_480 + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$treatments == "pasture",])

model_selection_herb_det_SS4_post_hoc_isolation_pasture <- aictab(list(mod_herb_det_SS4_no_effect_pasture,
                                                                       mod_herb_det_SS4_isolation_pasture,
                                                                       mod_herb_det_SS4_isolation30_120480_pasture,
                                                                       mod_herb_det_SS4_isolation30120_480_pasture),
                                                                  modnames = c("No Effect",
                                                                               "30 # 120 # 480",
                                                                               "30 # (120 = 480)",
                                                                               "(30 = 120) # 480"), sort = FALSE)


model_selection_herb_det_SS4_post_hoc_isolation_pasture


#sugarcane
mod_herb_det_SS4_no_effect_sugarcane <- glmmTMB(com_herb_det_ab_SS4[data_SS4$treatments == "sugar_cane"] ~  1 + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$treatments == "sugar_cane",])
mod_herb_det_SS4_isolation_sugarcane <- glmmTMB(com_herb_det_ab_SS4[data_SS4$treatments == "sugar_cane"] ~  isolation + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$treatments == "sugar_cane",])
mod_herb_det_SS4_isolation30_120480_sugarcane  <- glmmTMB(com_herb_det_ab_SS4[data_SS4$treatments == "sugar_cane"] ~  isolation30_120480 + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$treatments == "sugar_cane",])
mod_herb_det_SS4_isolation30120_480_sugarcane  <- glmmTMB(com_herb_det_ab_SS4[data_SS4$treatments == "sugar_cane"] ~  isolation30120_480 + (1|ID), family = nbinom2(link = "log"), data = data_SS4[data_SS4$treatments == "sugar_cane",])

model_selection_herb_det_SS4_post_hoc_isolation_sugarcane <- aictab(list(mod_herb_det_SS4_no_effect_sugarcane,
                                                                       mod_herb_det_SS4_isolation_sugarcane,
                                                                       mod_herb_det_SS4_isolation30_120480_sugarcane,
                                                                       mod_herb_det_SS4_isolation30120_480_sugarcane),
                                                                  modnames = c("No Effect",
                                                                               "30 # 120 # 480",
                                                                               "30 # (120 = 480)",
                                                                               "(30 = 120) # 480"), sort = FALSE)

model_selection_herb_det_SS4_post_hoc_isolation_sugarcane

```
We can consider that only isolation is important only for pasture and sugarcane ponds. In both, 30m is different from 120 and 480m.



```{r, dpi=150, fig.width=3, fig.height=3, fig.align = 'center', warning=FALSE}
par(mar = c(3.5, 4, 0.1, 0.1)+ 0.1, cex = 0.7, bty = "l")

boxplot(com_herb_det_ab_SS4 ~ treatments_SS2_3_4*isolation_SS2_3_4, outline = T,
        ylab = "", xlab = "", at = c(1,2,3, 5,6,7, 9,10,11), lwd = 0.5,
        main = "", xaxt="n", yaxt = "n", range = 1.5,
        col = rep(c(col_control, col_pasture, col_sugarcane),3), lty = 1,
        pch = 21, bg = rep(c(col_control, col_pasture, col_sugarcane),3), cex = 1,
        ylim = c(0,550))

title(ylab="Total Abundance", line=2.5, cex.lab=1.52)
#title(main= "Predatory Insects", adj = 1)
axis(2, cex.axis = 1, gap.axis = -1)
axis(1,labels = c("30 m","120 m","480 m"), cex.axis = 1.25, at =c(2,6,10), line = 0.5, tick = F, gap.axis = -1)
axis(1,labels = rep("",9), cex.axis = 0.8, at =c(1,2,3, 5,6,7, 9,10,11), line = 0,tick = T)

position1 <- 550

text(y = rep(position1, 9),x = c(1,2,3 ),
     labels = c("b","a","b"  ),
     cex = 1, adj = c(0.5,0.5),
     col = c("grey0","grey50","grey0"))

arrows(x0 = c(1, 2,3) - 0.4,
       y0 = rep(position1*0.95, 9),
       x1 = c(1, 2,3) + 0.4,
       y1 = rep(position1*0.95, 9),
       code = 0, col = c("grey0","grey50","grey0"))


```





