---
title: "Abundance Analyses - Herbivore and Detritivores - Insects"
author: "Rodolfo Pelinson"
date: "26/12/2022"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = TRUE, message=FALSE, warning=FALSE, warning=FALSE}
library(glmmTMB)
library(car)
library(emmeans)
library(DHARMa)
library(AICcmodavg)

```


Before anything, lets load and prepare some data sheets and vectors for the analysis.
```{r include = FALSE, warning=FALSE}
setwd("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/IsolationAgrochemicals")
source("Auxiliary scripts/Loading_data.R")
```



# Herbivores and Detritivores

First, lets make vectors of the abundances (summing up the abundance of all herb_det taxa in each sample):

```{r, warning=FALSE}



sum_com_herb_det_ab_SS1 <- rowSums(sum_com_orig_SS1[,which(Trait_SS1_sum_orig$trait == "insect_consumer")])
sum_com_herb_det_ab_SS2 <- rowSums(sum_com_orig_SS2[,which(Trait_SS2_sum_orig$trait == "insect_consumer")])
sum_com_herb_det_ab_SS3 <- rowSums(sum_com_orig_SS3[,which(Trait_SS3_sum_orig$trait == "insect_consumer")])
sum_com_herb_det_ab_SS4 <- rowSums(sum_com_orig_SS4[,which(Trait_SS4_sum_orig$trait == "insect_consumer")])

com_herb_det_ab_SS1 <- rowSums(com_SS1_orig[,which(Trait_SS1_orig$trait == "insect_consumer")])
com_herb_det_ab_SS2 <- rowSums(com_SS2_orig[,which(Trait_SS2_orig$trait == "insect_consumer")])
com_herb_det_ab_SS3 <- rowSums(com_SS3_orig[,which(Trait_SS3_orig$trait == "insect_consumer")])
com_herb_det_ab_SS4 <- rowSums(com_SS4_orig[,which(Trait_SS4_orig$trait == "insect_consumer")])

```


# First Survey (20 day)

Model Selection for mixed models
```{r, warning=FALSE}
data_SS1 <- data.frame(isolation = isolation_SS1, treatments = treatments_SS1)

mod_herb_det_SS1_no_effect <- glmmTMB(com_herb_det_ab_SS1 ~ 1, family = nbinom2(link = "log"), data = data_SS1)
mod_herb_det_SS1_treatments <- glmmTMB(com_herb_det_ab_SS1 ~ treatments, family = nbinom2(link = "log"), data = data_SS1)
mod_herb_det_SS1_isolation <- glmmTMB(com_herb_det_ab_SS1 ~ isolation, family = nbinom2(link = "log"), data = data_SS1)
mod_herb_det_SS1_isolation_treatments <- glmmTMB(com_herb_det_ab_SS1 ~ isolation + treatments, family = nbinom2(link = "log"), data = data_SS1)
mod_herb_det_SS1_isolation_i_treatments <- glmmTMB(com_herb_det_ab_SS1 ~ isolation * treatments, family = nbinom2(link = "log"), data = data_SS1)

model_selection_herb_det_SS1 <- aictab(list(mod_herb_det_SS1_no_effect,
                                             mod_herb_det_SS1_treatments,
                                             mod_herb_det_SS1_isolation,
                                             mod_herb_det_SS1_isolation_treatments,
                                             mod_herb_det_SS1_isolation_i_treatments),
                                        modnames = c("No Effect",
                                                     "Treatments",
                                                     "Isolation",
                                                     "Treatments + Isolation",
                                                     "Treatments * Isolation"), sort = FALSE)

model_selection_herb_det_SS1
```
Effect of isolation


```{r}
mod_herb_det_SS1_treatments <- glmmTMB(com_herb_det_ab_SS1 ~ treatments, family = nbinom2(link = "log"), data = data_SS1)
mod_herb_det_SS1_isolation <- glmmTMB(com_herb_det_ab_SS1 ~ isolation, family = nbinom2(link = "log"), data = data_SS1)
mod_herb_det_SS1_isolation_treatments <- glmmTMB(com_herb_det_ab_SS1 ~ isolation + treatments, family = nbinom2(link = "log"), data = data_SS1)
mod_herb_det_SS1_isolation_i_treatments <- glmmTMB(com_herb_det_ab_SS1 ~ isolation * treatments, family = nbinom2(link = "log"), data = data_SS1)

#Isolation
anova(mod_herb_det_SS1_treatments, mod_herb_det_SS1_isolation_treatments)

#Treatments
anova(mod_herb_det_SS1_isolation, mod_herb_det_SS1_isolation_treatments)

#Interaction
anova(mod_herb_det_SS1_isolation_treatments, mod_herb_det_SS1_isolation_i_treatments)
```
Effect of isolation, and a weird effect of interaction. 





# Second Survey (40 day)

### Mixed models

Model Selection for mixed models
```{r, warning=FALSE}
data_SS2 <- data.frame(ID = ID_SS2_3_4, isolation = isolation_SS2_3_4, treatments = treatments_SS2_3_4)


mod_herb_det_SS2_no_effect <- glmmTMB(com_herb_det_ab_SS2 ~ 1 + (1|ID), family = nbinom2(link = "log"), data = data_SS2)
mod_herb_det_SS2_treatments <- glmmTMB(com_herb_det_ab_SS2 ~ treatments + (1|ID), family = nbinom2(link = "log"), data = data_SS2)
mod_herb_det_SS2_isolation <- glmmTMB(com_herb_det_ab_SS2 ~ isolation + (1|ID), family = nbinom2(link = "log"), data = data_SS2)
mod_herb_det_SS2_isolation_treatments <- glmmTMB(com_herb_det_ab_SS2 ~ isolation + treatments + (1|ID), family = nbinom2(link = "log"), data = data_SS2)
mod_herb_det_SS2_isolation_i_treatments <- glmmTMB(com_herb_det_ab_SS2 ~ isolation * treatments + (1|ID), family = nbinom2(link = "log"), data = data_SS2)

model_selection_herb_det_SS2 <- aictab(list(mod_herb_det_SS2_no_effect,
                                             mod_herb_det_SS2_treatments,
                                             mod_herb_det_SS2_isolation,
                                             mod_herb_det_SS2_isolation_treatments,
                                             mod_herb_det_SS2_isolation_i_treatments),
                                        modnames = c("No Effect",
                                                     "Treatments",
                                                     "Isolation",
                                                     "Treatments + Isolation",
                                                     "Treatments * Isolation"), sort = FALSE)

model_selection_herb_det_SS2
```
Effect of isolation and agrochemical treatments

LRT for mixed models
```{r}
mod_herb_det_SS2_treatments <- glmmTMB(com_herb_det_ab_SS2 ~ treatments+ (1|ID), family = nbinom2(link = "log"), data = data_SS2)
mod_herb_det_SS2_isolation <- glmmTMB(com_herb_det_ab_SS2 ~ isolation+ (1|ID), family = nbinom2(link = "log"), data = data_SS2)
mod_herb_det_SS2_isolation_treatments <- glmmTMB(com_herb_det_ab_SS2 ~ isolation + treatments+ (1|ID), family = nbinom2(link = "log"), data = data_SS2)
mod_herb_det_SS2_isolation_i_treatments <- glmmTMB(com_herb_det_ab_SS2 ~ isolation * treatments+ (1|ID), family = nbinom2(link = "log"), data = data_SS2)

#Isolation
anova(mod_herb_det_SS2_treatments, mod_herb_det_SS2_isolation_treatments)

#Treatments
anova(mod_herb_det_SS2_isolation, mod_herb_det_SS2_isolation_treatments)

#Interaction
anova(mod_herb_det_SS2_isolation_treatments, mod_herb_det_SS2_isolation_i_treatments)
```
Effect of isolation and agrochemical treatments


### Models pooling samples together

Model Selection for mixed models
```{r, warning=FALSE}
data_SS2_sum <- data.frame(ID = ID_SS1, isolation = isolation_SS1, treatments = treatments_SS1)

mod_herb_det_SS2_no_effect_sum <- glmmTMB(sum_com_herb_det_ab_SS2 ~ 1 , family = nbinom2(link = "log"), data = data_SS2_sum)
mod_herb_det_SS2_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS2 ~ treatments , family = nbinom2(link = "log"), data = data_SS2_sum)
mod_herb_det_SS2_isolation_sum <- glmmTMB(sum_com_herb_det_ab_SS2 ~ isolation , family = nbinom2(link = "log"), data = data_SS2_sum)
mod_herb_det_SS2_isolation_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS2 ~ isolation + treatments , family = nbinom2(link = "log"), data = data_SS2_sum)
mod_herb_det_SS2_isolation_i_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS2 ~ isolation * treatments , family = nbinom2(link = "log"), data = data_SS2_sum)

model_selection_herb_det_SS2_sum <- aictab(list(mod_herb_det_SS2_no_effect_sum,
                                             mod_herb_det_SS2_treatments_sum,
                                             mod_herb_det_SS2_isolation_sum,
                                             mod_herb_det_SS2_isolation_treatments_sum,
                                             mod_herb_det_SS2_isolation_i_treatments_sum),
                                        modnames = c("No Effect",
                                                     "Treatments",
                                                     "Isolation",
                                                     "Treatments + Isolation",
                                                     "Treatments * Isolation"), sort = FALSE)

model_selection_herb_det_SS2_sum
```
Effect of isolation and agrochemical treatments

LRT for mixed models
```{r}
mod_herb_det_SS2_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS2 ~ treatments, family = nbinom2(link = "log"), data = data_SS2_sum)
mod_herb_det_SS2_isolation_sum <- glmmTMB(sum_com_herb_det_ab_SS2 ~ isolation, family = nbinom2(link = "log"), data = data_SS2_sum)
mod_herb_det_SS2_isolation_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS2 ~ isolation + treatments, family = nbinom2(link = "log"), data = data_SS2_sum)
mod_herb_det_SS2_isolation_i_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS2 ~ isolation * treatments, family = nbinom2(link = "log"), data = data_SS2_sum)

#Isolation
anova(mod_herb_det_SS2_treatments_sum, mod_herb_det_SS2_isolation_treatments_sum)

#Treatments
anova(mod_herb_det_SS2_isolation_sum, mod_herb_det_SS2_isolation_treatments_sum)

#Interaction
anova(mod_herb_det_SS2_isolation_treatments_sum, mod_herb_det_SS2_isolation_i_treatments_sum)
```
Effect of isolation and agrochemical treatments.









# Third Survey (80 day)

### Mixed models

Model Selection for mixed models
```{r, warning=FALSE}
data_SS3 <- data.frame(ID = ID_SS2_3_4, isolation = isolation_SS2_3_4, treatments = treatments_SS2_3_4)


mod_herb_det_SS3_no_effect <- glmmTMB(com_herb_det_ab_SS3 ~ 1 + (1|ID), family = nbinom2(link = "log"), data = data_SS3)
mod_herb_det_SS3_treatments <- glmmTMB(com_herb_det_ab_SS3 ~ treatments + (1|ID), family = nbinom2(link = "log"), data = data_SS3)
mod_herb_det_SS3_isolation <- glmmTMB(com_herb_det_ab_SS3 ~ isolation + (1|ID), family = nbinom2(link = "log"), data = data_SS3)
mod_herb_det_SS3_isolation_treatments <- glmmTMB(com_herb_det_ab_SS3 ~ isolation + treatments + (1|ID), family = nbinom2(link = "log"), data = data_SS3)
mod_herb_det_SS3_isolation_i_treatments <- glmmTMB(com_herb_det_ab_SS3 ~ isolation * treatments + (1|ID), family = nbinom2(link = "log"), data = data_SS3)

model_selection_herb_det_SS3 <- aictab(list(mod_herb_det_SS3_no_effect,
                                             mod_herb_det_SS3_treatments,
                                             mod_herb_det_SS3_isolation,
                                             mod_herb_det_SS3_isolation_treatments,
                                             mod_herb_det_SS3_isolation_i_treatments),
                                        modnames = c("No Effect",
                                                     "Treatments",
                                                     "Isolation",
                                                     "Treatments + Isolation",
                                                     "Treatments * Isolation"), sort = FALSE)

model_selection_herb_det_SS3
```
Effect of isolation and agrochemical treatments.

LRT for mixed models
```{r}
mod_herb_det_SS3_treatments <- glmmTMB(com_herb_det_ab_SS3 ~ treatments+ (1|ID), family = nbinom2(link = "log"), data = data_SS3)
mod_herb_det_SS3_isolation <- glmmTMB(com_herb_det_ab_SS3 ~ isolation+ (1|ID), family = nbinom2(link = "log"), data = data_SS3)
mod_herb_det_SS3_isolation_treatments <- glmmTMB(com_herb_det_ab_SS3 ~ isolation + treatments+ (1|ID), family = nbinom2(link = "log"), data = data_SS3)
mod_herb_det_SS3_isolation_i_treatments <- glmmTMB(com_herb_det_ab_SS3 ~ isolation * treatments+ (1|ID), family = nbinom2(link = "log"), data = data_SS3)

#Isolation
anova(mod_herb_det_SS3_treatments, mod_herb_det_SS3_isolation_treatments)

#Treatments
anova(mod_herb_det_SS3_isolation, mod_herb_det_SS3_isolation_treatments)

#Interaction
anova(mod_herb_det_SS3_isolation_treatments, mod_herb_det_SS3_isolation_i_treatments)
```
Effect of isolation and agrochemical treatments.


### Models pooling samples together

Model Selection for mixed models
```{r, warning=FALSE}
data_SS3_sum <- data.frame(ID = ID_SS1, isolation = isolation_SS1, treatments = treatments_SS1)

mod_herb_det_SS3_no_effect_sum <- glmmTMB(sum_com_herb_det_ab_SS3 ~ 1 , family = nbinom2(link = "log"), data = data_SS3_sum)
mod_herb_det_SS3_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS3 ~ treatments , family = nbinom2(link = "log"), data = data_SS3_sum)
mod_herb_det_SS3_isolation_sum <- glmmTMB(sum_com_herb_det_ab_SS3 ~ isolation , family = nbinom2(link = "log"), data = data_SS3_sum)
mod_herb_det_SS3_isolation_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS3 ~ isolation + treatments , family = nbinom2(link = "log"), data = data_SS3_sum)
mod_herb_det_SS3_isolation_i_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS3 ~ isolation * treatments , family = nbinom2(link = "log"), data = data_SS3_sum)

model_selection_herb_det_SS3_sum <- aictab(list(mod_herb_det_SS3_no_effect_sum,
                                             mod_herb_det_SS3_treatments_sum,
                                             mod_herb_det_SS3_isolation_sum,
                                             mod_herb_det_SS3_isolation_treatments_sum,
                                             mod_herb_det_SS3_isolation_i_treatments_sum),
                                        modnames = c("No Effect",
                                                     "Treatments",
                                                     "Isolation",
                                                     "Treatments + Isolation",
                                                     "Treatments * Isolation"), sort = FALSE)

model_selection_herb_det_SS3_sum
```
Effect of isolation only.

LRT for mixed models
```{r}
mod_herb_det_SS3_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS3 ~ treatments, family = nbinom2(link = "log"), data = data_SS3_sum)
mod_herb_det_SS3_isolation_sum <- glmmTMB(sum_com_herb_det_ab_SS3 ~ isolation, family = nbinom2(link = "log"), data = data_SS3_sum)
mod_herb_det_SS3_isolation_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS3 ~ isolation + treatments, family = nbinom2(link = "log"), data = data_SS3_sum)
mod_herb_det_SS3_isolation_i_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS3 ~ isolation * treatments, family = nbinom2(link = "log"), data = data_SS3_sum)

#Isolation
anova(mod_herb_det_SS3_treatments_sum, mod_herb_det_SS3_isolation_treatments_sum)

#Treatments
anova(mod_herb_det_SS3_isolation_sum, mod_herb_det_SS3_isolation_treatments_sum)

#Interaction
anova(mod_herb_det_SS3_isolation_treatments_sum, mod_herb_det_SS3_isolation_i_treatments_sum)
```
Effect of isolation only.








# Fourth Survey (160 day)

### Mixed models

Model Selection for mixed models
```{r, warning=FALSE}
data_SS4 <- data.frame(ID = ID_SS2_3_4, isolation = isolation_SS2_3_4, treatments = treatments_SS2_3_4)


mod_herb_det_SS4_no_effect <- glmmTMB(com_herb_det_ab_SS4 ~ 1 + (1|ID), family = nbinom2(link = "log"), data = data_SS4)
mod_herb_det_SS4_treatments <- glmmTMB(com_herb_det_ab_SS4 ~ treatments + (1|ID), family = nbinom2(link = "log"), data = data_SS4)
mod_herb_det_SS4_isolation <- glmmTMB(com_herb_det_ab_SS4 ~ isolation + (1|ID), family = nbinom2(link = "log"), data = data_SS4)
mod_herb_det_SS4_isolation_treatments <- glmmTMB(com_herb_det_ab_SS4 ~ isolation + treatments + (1|ID), family = nbinom2(link = "log"), data = data_SS4)
mod_herb_det_SS4_isolation_i_treatments <- glmmTMB(com_herb_det_ab_SS4 ~ isolation * treatments + (1|ID), family = nbinom2(link = "log"), data = data_SS4)

model_selection_herb_det_SS4 <- aictab(list(mod_herb_det_SS4_no_effect,
                                             mod_herb_det_SS4_treatments,
                                             mod_herb_det_SS4_isolation,
                                             mod_herb_det_SS4_isolation_treatments,
                                             mod_herb_det_SS4_isolation_i_treatments),
                                        modnames = c("No Effect",
                                                     "Treatments",
                                                     "Isolation",
                                                     "Treatments + Isolation",
                                                     "Treatments * Isolation"), sort = FALSE)

model_selection_herb_det_SS4
```
Interactive effects.

LRT for mixed models
```{r}
mod_herb_det_SS4_treatments <- glmmTMB(com_herb_det_ab_SS4 ~ treatments+ (1|ID), family = nbinom2(link = "log"), data = data_SS4)
mod_herb_det_SS4_isolation <- glmmTMB(com_herb_det_ab_SS4 ~ isolation+ (1|ID), family = nbinom2(link = "log"), data = data_SS4)
mod_herb_det_SS4_isolation_treatments <- glmmTMB(com_herb_det_ab_SS4 ~ isolation + treatments+ (1|ID), family = nbinom2(link = "log"), data = data_SS4)
mod_herb_det_SS4_isolation_i_treatments <- glmmTMB(com_herb_det_ab_SS4 ~ isolation * treatments+ (1|ID), family = nbinom2(link = "log"), data = data_SS4)

#Isolation
anova(mod_herb_det_SS4_treatments, mod_herb_det_SS4_isolation_treatments)

#Treatments
anova(mod_herb_det_SS4_isolation, mod_herb_det_SS4_isolation_treatments)

#Interaction
anova(mod_herb_det_SS4_isolation_treatments, mod_herb_det_SS4_isolation_i_treatments)
```
Interactive effects.


### Models pooling samples together

Model Selection for mixed models
```{r, warning=FALSE}
data_SS4_sum <- data.frame(ID = ID_SS1, isolation = isolation_SS1, treatments = treatments_SS1)

mod_herb_det_SS4_no_effect_sum <- glmmTMB(sum_com_herb_det_ab_SS4 ~ 1 , family = nbinom2(link = "log"), data = data_SS4_sum)
mod_herb_det_SS4_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS4 ~ treatments , family = nbinom2(link = "log"), data = data_SS4_sum)
mod_herb_det_SS4_isolation_sum <- glmmTMB(sum_com_herb_det_ab_SS4 ~ isolation , family = nbinom2(link = "log"), data = data_SS4_sum)
mod_herb_det_SS4_isolation_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS4 ~ isolation + treatments , family = nbinom2(link = "log"), data = data_SS4_sum)
mod_herb_det_SS4_isolation_i_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS4 ~ isolation * treatments , family = nbinom2(link = "log"), data = data_SS4_sum)

model_selection_herb_det_SS4_sum <- aictab(list(mod_herb_det_SS4_no_effect_sum,
                                             mod_herb_det_SS4_treatments_sum,
                                             mod_herb_det_SS4_isolation_sum,
                                             mod_herb_det_SS4_isolation_treatments_sum,
                                             mod_herb_det_SS4_isolation_i_treatments_sum),
                                        modnames = c("No Effect",
                                                     "Treatments",
                                                     "Isolation",
                                                     "Treatments + Isolation",
                                                     "Treatments * Isolation"), sort = FALSE)

model_selection_herb_det_SS4_sum
```
Interactive effects is the most plausible model, but the model with no effects is also plausible.

LRT for mixed models.
```{r}
mod_herb_det_SS4_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS4 ~ treatments, family = nbinom2(link = "log"), data = data_SS4_sum)
mod_herb_det_SS4_isolation_sum <- glmmTMB(sum_com_herb_det_ab_SS4 ~ isolation, family = nbinom2(link = "log"), data = data_SS4_sum)
mod_herb_det_SS4_isolation_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS4 ~ isolation + treatments, family = nbinom2(link = "log"), data = data_SS4_sum)
mod_herb_det_SS4_isolation_i_treatments_sum <- glmmTMB(sum_com_herb_det_ab_SS4 ~ isolation * treatments, family = nbinom2(link = "log"), data = data_SS4_sum)

#Isolation
anova(mod_herb_det_SS4_treatments_sum, mod_herb_det_SS4_isolation_treatments_sum)

#Treatments
anova(mod_herb_det_SS4_isolation_sum, mod_herb_det_SS4_isolation_treatments_sum)

#Interaction
anova(mod_herb_det_SS4_isolation_treatments_sum, mod_herb_det_SS4_isolation_i_treatments_sum)
```
Interactive effects.



