---
title: "Nutrients"
author: "Rodolfo Pelinson"
date: "03/01/2023"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo = TRUE, message=FALSE, warning=FALSE}
library(glmmTMB)
library(car)
library(emmeans)
library(DHARMa)
library(bbmle)
library(AICcmodavg)

```

```{r include = FALSE}
setwd("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/IsolationAgrochemicals")
nutrients <- read.csv("Data/Nutrients.csv")
source("Auxiliary scripts/Loading_data.R")
```



```{r}
nutrients$treatment <- factor(nutrients$treatment, levels = c("control","pasture","sugarcane"))
nutrients$isolation <- factor(as.character(nutrients$isolation), levels = c("30","120","480"))
nutrients$treatments_cont_pastsug <- treatments_cont_pastsug
nutrients$treatments_contpast_sug <- treatments_contpast_sug
nutrients$treatments_contsug_past <- treatments_contsug_past
nutrients$isolation30_120480 <- isolation30_120480
nutrients$isolation30120_480 <- isolation30120_480

```


# Phosphorus

First the analysis of total phosphorus concentration in surface water 73 days after the beginning of nutrient addition in pasture and sugarcane ponds.
```{r, dpi=150, fig.width=3, fig.height=3, fig.align = 'center', warning=FALSE}
par(cex = 0.6)


mod_P_third_GAUSSIAN <- glmmTMB(P_ug_L ~ treatment * isolation, data = nutrients, family = "gaussian")

simulationResiduals_mod_P_third_GAUSSIAN <- simulateResiduals(fittedModel = mod_P_third_GAUSSIAN, plot = F, seed = 3, n = 1000)
plotQQunif(simulationResiduals_mod_P_third_GAUSSIAN, testUniformity = F, testOutliers = F, testDispersion = F, cex.lab = 1.5, cex.main = 1.5)
plotResiduals(simulationResiduals_mod_P_third_GAUSSIAN,  quantreg = F, cex.lab = 1.5, cex.main = 1.5)

mod_P_third_GAMMA <- glmmTMB(P_ug_L ~ treatment * isolation, data = nutrients, family = Gamma(link = "log"))

simulationResiduals_mod_P_third_GAMMA <- simulateResiduals(fittedModel = mod_P_third_GAMMA, plot = F, seed = 3, n = 1000)
plotQQunif(simulationResiduals_mod_P_third_GAMMA, testUniformity = F, testOutliers = F, testDispersion = F, cex.lab = 1.5, cex.main = 1.5)
plotResiduals(simulationResiduals_mod_P_third_GAMMA,  quantreg = F, cex.lab = 1.5, cex.main = 1.5)

bbmle::AICctab(mod_P_third_GAUSSIAN, mod_P_third_GAMMA)



mod_P_no_effect <- glmmTMB(P_ug_L ~ 1, data = nutrients, family = Gamma(link = "log"))
mod_P_treatment <- glmmTMB(P_ug_L ~ treatment, data = nutrients, family = Gamma(link = "log"))
mod_P_isolation <- glmmTMB(P_ug_L ~ isolation, data = nutrients, family = Gamma(link = "log"))
mod_P_treatment_isolation <- glmmTMB(P_ug_L ~ treatment + isolation, data = nutrients, family = Gamma(link = "log"))
mod_P_treatment_I_isolation <- glmmTMB(P_ug_L ~ treatment * isolation, data = nutrients, family = Gamma(link = "log"))

aictab(list(mod_P_no_effect,
            mod_P_treatment,
            mod_P_isolation,
            mod_P_treatment_isolation,
            mod_P_treatment_I_isolation), modnames = c("No Effect",
                                                       "Treatments",
                                                       "Isolation",
                                                       "Isolation + Treatments",
                                                       "Isolamento * Treatments"), sort = FALSE)

mod_P_treatment <- glmmTMB(P_ug_L ~ isolation + treatment, family = Gamma(link = "log"), data = nutrients)
mod_P_treatments_cont_pastsug <- glmmTMB(P_ug_L ~ isolation + treatments_cont_pastsug, family = Gamma(link = "log"), data = nutrients)
mod_P_treatments_contpast_sug <- glmmTMB(P_ug_L ~ isolation + treatments_contpast_sug, family = Gamma(link = "log"), data = nutrients)
mod_P_treatments_contsug_past <- glmmTMB(P_ug_L ~ isolation + treatments_contsug_past, family = Gamma(link = "log"), data = nutrients)


aictab(list(mod_P_treatment,
            mod_P_treatments_contpast_sug,
            mod_P_treatments_cont_pastsug,
            mod_P_treatments_contsug_past), modnames = c("Savanna # Pasture # Sugarcane",
                                                       "(Savanna = Pasture) # Sugarcane",
                                                       "Savanna # (Pasture = Sugarcane)",
                                                       "(Savanna = Sugarcane) # Pasture"))


```
Looks like the phosphorus concentration in sugarcane ponds is higher than in pasture and control ponds.


Plotting it. The grey hatched line is the threshold concentration for hypertrophic lakes.
```{r, dpi=150, fig.width=3, fig.height=3, fig.align = 'center', warning=FALSE}
tratment_by_isolation <- interaction(nutrients$treatment, nutrients$isolation)

par(mar = c(4,5,2,2), cex = 0.7)
boxplot(P_ug_L ~ treatment, data = nutrients,
        ylab = expression(paste("P (", mu, "g ", L^-1,")")),
        xlab = "", cex.lab = 1.3,
        col = "transparent", main = "73 days", xaxt="n", yaxt = "n", outline = F, ylim = c(0,500))
axis(2, cex.axis = 1, gap.axis = -1)

mylevels <- levels(tratment_by_isolation)
levelProportions <- summary(tratment_by_isolation)/length(tratment_by_isolation)
col <- c("steelblue1", "palegreen2","orange2","steelblue3","palegreen3","orange3","steelblue4", "palegreen4","orange4")
pch <- c(15,15,15,16,16,16,17,17,17)

for(i in 1:length(mylevels)){

  x<- c(1,2,3, 1,2,3, 1,2,3)[i]

  thislevel <- mylevels[i]
  thisvalues <- nutrients$P_ug_L[tratment_by_isolation==thislevel]

  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.5)
  points(myjitter, thisvalues, pch=pch[i], col=col[i] , cex = 1, lwd = 3)
}

boxplot(P_ug_L ~ treatment, data = nutrients,
        col = "transparent", xaxt="n", yaxt = "n", outline = F, add = TRUE)


axis(1, at = 1:3, labels = F, tick = T, line = 0)
axis(1, at = 1:3, labels = c("Control","Pasture", "Sugarcane"), tick = F, line = 0, cex.axis = 1.2)
abline(h = 100, lty = 2, lwd = 2, col = "grey50")

```






# Nitrogen

Now, the analysis of total nitrogen concentration in surface water 73 days after the beginning of nutrient addition in pasture and sugarcane ponds.

```{r, dpi=150, fig.width=3, fig.height=3, fig.align = 'center', warning=FALSE}
par(cex = 0.6)

mod_TN_third_GAUSSIAN <- glmmTMB(TN_mg_L ~ treatment * isolation, data = nutrients, family = "gaussian")

simulationResiduals_mod_TN_third_GAUSSIAN <- simulateResiduals(fittedModel = mod_TN_third_GAUSSIAN, plot = F, seed = 3, n = 1000)
plotQQunif(simulationResiduals_mod_TN_third_GAUSSIAN, testUniformity = F, testOutliers = F, testDispersion = F, cex.lab = 1.5, cex.main = 1.5)
plotResiduals(simulationResiduals_mod_TN_third_GAUSSIAN,  quantreg = F, cex.lab = 1.5, cex.main = 1.5)

mod_TN_third_GAMMA <- glmmTMB(TN_mg_L ~ treatment * isolation, data = nutrients, family = Gamma(link = "log"))

simulationResiduals_mod_TN_third_GAMMA <- simulateResiduals(fittedModel = mod_TN_third_GAMMA, plot = F, seed = 3, n = 1000)
plotQQunif(simulationResiduals_mod_TN_third_GAMMA, testUniformity = F, testOutliers = F, testDispersion = F, cex.lab = 1.5, cex.main = 1.5)
plotResiduals(simulationResiduals_mod_TN_third_GAMMA,  quantreg = F, cex.lab = 1.5, cex.main = 1.5)


bbmle::AICctab(mod_TN_third_GAUSSIAN, mod_TN_third_GAMMA)



mod_N_no_effect <- glmmTMB(TN_mg_L ~ 1, data = nutrients, family = Gamma(link = "log"))
mod_N_treatment <- glmmTMB(TN_mg_L ~ treatment, data = nutrients, family = Gamma(link = "log"))
mod_N_isolation <- glmmTMB(TN_mg_L ~ isolation, data = nutrients, family = Gamma(link = "log"))
mod_N_treatment_isolation <- glmmTMB(TN_mg_L ~ treatment + isolation, data = nutrients, family = Gamma(link = "log"))
mod_N_treatment_I_isolation <- glmmTMB(TN_mg_L ~ treatment * isolation, data = nutrients, family = Gamma(link = "log"))

aictab(list(mod_N_no_effect,
            mod_N_treatment,
            mod_N_isolation,
            mod_N_treatment_isolation,
            mod_N_treatment_I_isolation), modnames = c("No Effect",
                                                       "Treatments",
                                                       "Isolation",
                                                       "Isolation + Treatments",
                                                       "Isolamento * Treatments"), sort = FALSE)

mod_N_treatment <- glmmTMB(TN_mg_L ~ isolation + treatment, family = Gamma(link = "log"), data = nutrients)
mod_N_treatments_cont_pastsug <- glmmTMB(TN_mg_L ~ isolation + treatments_cont_pastsug, family = Gamma(link = "log"), data = nutrients)
mod_N_treatments_contpast_sug <- glmmTMB(TN_mg_L ~ isolation + treatments_contpast_sug, family = Gamma(link = "log"), data = nutrients)
mod_N_treatments_contsug_past <- glmmTMB(TN_mg_L ~ isolation + treatments_contsug_past, family = Gamma(link = "log"), data = nutrients)


aictab(list(mod_N_treatment,
            mod_N_treatments_contpast_sug,
            mod_N_treatments_cont_pastsug,
            mod_N_treatments_contsug_past), modnames = c("Savanna # Pasture # Sugarcane",
                                                       "(Savanna = Pasture) # Sugarcane",
                                                       "Savanna # (Pasture = Sugarcane)",
                                                       "(Savanna = Sugarcane) # Pasture"))



mod_N_isolation <- glmmTMB(TN_mg_L ~ isolation + treatment, family = Gamma(link = "log"), data = nutrients)
mod_N_isolation_30_120480 <- glmmTMB(TN_mg_L ~ treatment + isolation30_120480, family = Gamma(link = "log"), data = nutrients)
mod_N_isolation_30120_480 <- glmmTMB(TN_mg_L ~ treatment + isolation30120_480, family = Gamma(link = "log"), data = nutrients)


aictab(list(mod_N_isolation,
            mod_N_isolation_30120_480,
            mod_N_isolation_30_120480), modnames = c("30 # 120 # 480",
                                                       "(30 = 120) # 480",
                                                       "30 # (120 = 480)"))


```
Looks like the nitrogen concentration in sugarcane ponds is higher than in pasture and control ponds. Also, it is higher 480m than in 30 and 120m.


Plotting it. The grey hatched line is the threshold concentration for hypertrophic lakes.
```{r, dpi=150, fig.width=9, fig.height=3, fig.align = 'center', warning=FALSE}
tratment_by_isolation <- interaction(nutrients$treatment, nutrients$isolation)


par(mar = c(4,5,2,2), cex = 0.7)
boxplot(TN_mg_L ~ treatment*isolation, data = nutrients,
        ylab = expression(paste("TN (mg ", L^-1,")")),
        xlab = "", cex.lab = 1.3,
        col = "transparent", main = "73 days", xaxt="n", yaxt = "n", outline = F, ylim = c(1,13), at = c(1,2,3 ,5,6,7, 9,10,11))
axis(2, cex.axis = 1, gap.axis = -1)

mylevels <- levels(tratment_by_isolation)
levelProportions <- summary(tratment_by_isolation)/length(tratment_by_isolation)
col <- c("steelblue1", "palegreen2","orange2","steelblue3","palegreen3","orange3","steelblue4", "palegreen4","orange4")
pch <- c(15,15,15,16,16,16,17,17,17)

for(i in 1:length(mylevels)){

  x<- c(1,2,3 ,5,6,7, 9,10,11)[i]

  thislevel <- mylevels[i]
  thisvalues <- nutrients$TN_mg_L[tratment_by_isolation==thislevel]

  # take the x-axis indices and add a jitter, proportional to the N in each level
  myjitter <- jitter(rep(x, length(thisvalues)), amount=levelProportions[i]/0.5)
  points(myjitter, thisvalues, pch=pch[i], col=col[i] , cex = 1, lwd = 3)
}

boxplot(TN_mg_L ~ treatment*isolation, data = nutrients,
        col = "transparent", xaxt="n", yaxt = "n", outline = F, add = TRUE, at = c(1,2,3 ,5,6,7, 9,10,11))


axis(1, at = c(1,2,3 ,5,6,7, 9,10,11), labels = F, tick = T, line = 0)
axis(1, at = c(1,2,3 ,5,6,7, 9,10,11), labels = rep(c("Control","Pasture", "Sugarcane"),3), tick = F, line = 0, cex.axis = 1, gap.axis = -1)
axis(1, at = c(2,6,10), labels = c("30 m","120 m", "480 m"), tick = F, line = 1.5, cex.axis = 1.2)

abline(h = 1.2, lty = 2, lwd = 2, col = "grey50")

```
