---
title: "Community Structure - Predatory Insects"
author: "Rodolfo Pelinson"
date: "27/12/2022"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = TRUE, message=FALSE, warning=FALSE}
library(vegan)
library(gllvm)
```

```{r include = FALSE}
setwd("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/IsolationAgrochemicals")
source("Auxiliary scripts/Loading_data.R")
source("Auxiliary scripts/Ordination_plots.R")

```


Before anything, here are three functions that will automate most of the model selection procedures that we will be doing. The script would be gigantic without them.

This first one is just to make a model selection table based on AICc for gllvm models. All functions rely on the gllvm function from the `gllvm` version 1.3.1 (it may need adjustments for other versions).
```{r}
setwd("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/IsolationAgrochemicals")
source("Auxiliary scripts/gllvm_AICc_tab.R")
```


This one is to run multiple gllvms with different number of latent variables and perform model selection. Its useful to find the ideal number of latent variables necessary to accurately account for correlations (dependencies) in species co-occurrences not caused by our treatments.
```{r}
setwd("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/IsolationAgrochemicals")
source("Auxiliary scripts/run_multiple_lv.R")
```


This is to automate running multiple gllvms and perform model selection
```{r}
setwd("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/IsolationAgrochemicals")
source("Auxiliary scripts/run_multiple_gllvm.R")
```


This is for getting scaled latent variables for plotting model based ordinations. I took most of code from the plotting functions from the `gllvm` package.
```{r}
setwd("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/IsolationAgrochemicals")
source("Auxiliary scripts/get_scaled_lvs.R")
```

This is for ploting species coefficients and their confidence intervals based on the effects identified in the analysis. The script for extracting these coefficients and the function for plotting is rather extensive, thus I will source the code on a script in the Auxiliary Scripts folder. You can check the original code there.
```{r, warning=FALSE}
setwd("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/IsolationAgrochemicals")
source("Auxiliary scripts/coefficients for predators.R")
source("Auxiliary scripts/My_coefplot.R")
```




# Predatory insects

Lets make tables with only predatory insects. Note that here we excludes species that occur in less than 4 samples in each survey because are less informative to community patterns and complicate parameter estimation.

```{r, warning=FALSE}

#cheking if the order of row in Trait_og and columns in com_orig match

data.frame(com = colnames(com), trait = Trait$genus)

com_predators <- com[,Trait$trophic == "predator"]
com_predators_SS1 <- com_SS1[,Trait_SS1$trophic == "predator"]
com_predators_SS2 <- com_SS2[,Trait_SS2$trophic == "predator"]
com_predators_SS3 <- com_SS3[,Trait_SS3$trophic == "predator"]
com_predators_SS4 <- com_SS4[,Trait_SS4$trophic == "predator"]

```


## All surveys

We always used a negative binomial distribution to model species abundances.
```{r}
predictors <- data.frame(ID = ID,
                         treatments = treatments_all,
                         isolation = isolation_all,
                         survey = SS,
                         survey_12_3_4 = SS_12_3_4,
                         survey_1_2_34 = SS_1_2_34,
                         survey_1_23_4 = SS_1_23_4,
                         survey_123_4 = SS_123_4,
                         survey_1_234 = SS_1_234)
```


Number of latent variables:
```{r, warning=FALSE, cache = TRUE}
n_latent_tab <- run_multiple_lv(formula = ~ treatments * isolation * survey,
                                    num.lv = c(0,1,2,3),
                                    row.eff = ~ (1|ID),
                                    y = com_predators, X = predictors,
                                    family = "negative.binomial",
                                    method = "VA",
                                    n.init = 10, seed = 1:10)

n_latent_tab$AICc_tab

```
It looks that zero latent variables is the way to go. This will repeat itself for the next cases.


Model selection of effects:
```{r, warning=FALSE, cache = TRUE}
model_predators_selection <- run_multiple_gllvm(formulas = list(    ~ survey,
                                                                    ~ treatments * isolation,
                                                                    ~ survey + (treatments * isolation),
                                                                    ~ survey * (treatments * isolation)),
                                                    names = c("Survey",
                                                              "Isolation * Treatments",
                                                              "Survey + (Isolation * Treatments)",
                                                              "Survey * (Isolation * Treatments)"),
                                                    no_effect = TRUE,
                                                    num.lv = 0,
                                                    row.eff = ~ (1|ID),
                                                    X_row = data.frame(ID = ID),
                                                    X = predictors,
                                                    y = com_predators,
                                                    family = "negative.binomial",
                                                    method = "VA",
                                                    n.init = 10, seed = 1:10)

model_predators_selection$AICc_tab
```
It seems that the effect of treatments is different in each survey.



```{r, warning=FALSE, cache = TRUE}
model_predators_selection_surveys <- run_multiple_gllvm(formulas = list(    ~ survey * (treatments * isolation),
                                                                    ~ survey_12_3_4 * (treatments * isolation),
                                                                    ~ survey_1_2_34 * (treatments * isolation),
                                                                    ~ survey_1_23_4 * (treatments * isolation),
                                                                    ~ survey_123_4 * (treatments * isolation),
                                                                    ~ survey_1_234 * (treatments * isolation)),
                                                    names = c("1 # 2 # 3 # 4",
                                                              "(1 = 2) # 3 # 4",
                                                              "1 # 2 # (3 = 4)",
                                                              "1 # (2 = 3) # 4",
                                                              "(1 = 2 = 3) # 4",
                                                              "1 # (2 = 3 = 4)"),
                                                    no_effect = FALSE,
                                                    num.lv = 0,
                                                    row.eff = ~ (1|ID),
                                                    X_row = data.frame(ID = ID),
                                                    X = predictors,
                                                    y = com_predators,
                                                    family = "negative.binomial",
                                                    method = "VA",
                                                    n.init = 10, seed = 1:10)

model_predators_selection_surveys$AICc_tab
```
All surveys are different from each other


Plot emphasizing effects of survey only. The code for plotting the ordinations is pretty extensive, I will then only show the first one as an example e call the others from functions sourced from the 'Auxiliary scripts" folder.
```{r, dpi=150, fig.width=4, fig.height=9, fig.align = 'center', warning=FALSE}

predictors <- data.frame(ID = rep(ID_SS1,4),
                         treatments = rep(treatments_SS1,4),
                         isolation = rep(isolation_SS1,4),
                         survey = as.factor(c(rep(1, 45), rep(2, 45), rep(3, 45), rep(4, 45))))


sum_com_predators <- sum_com[,Trait$trophic == "predator"]

col <- rep("lightsalmon1", ncol(sum_com_predators))

col_survey_1 <- "#0072B2"
col_survey_2 <- "#CC79A7"
col_survey_3 <- "#D55E00"
col_survey_4 <- "#DDCC77"



fit_plot <- gllvm(as.data.frame(sum_com_predators), X = data.frame(ID = predictors$ID),
                      formula = ~ 1,
                      family = "negative.binomial",
                      method = "VA",
                      row.eff = ~ (1|ID),
                      n.init = 10, num.lv = 2, seed = 1:10)


scaled_lvs <- get_scaled_lvs(fit_plot, alpha = 0.5)

set.seed(2)
scaled_lvs$species <- jitter(scaled_lvs$species, amount = 0.01)
set.seed(2)
scaled_lvs$sites <- jitter(scaled_lvs$sites, amount = 0.01)

scaled_lvs$new_species <- scaled_lvs$species/4


xmin <- min(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
xmax <- max(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
ymin <- min(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1 - 0.005
ymax <- max(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1 + 0.005


par(mar = c(4,4,1.25,.1),  mfrow = c(2,1), cex = 0.8)

  plot(NA,xlim = c(xmin, xmax), ylim = c(ymin, ymax), ylab = "LV2", xlab = "LV1", axes = F)
  axis(1 , gap.axis = -10)
  axis(2 , gap.axis = -10)
  abline(h=0,v=0, lty =2)

  ordiellipse(scaled_lvs$sites,
              groups = predictors$survey,
              draw = "polygon", border = FALSE,  col = c(col_survey_1, col_survey_2, col_survey_3, col_survey_4), kind = "sd", alpha = 50)

  #ordiellipse(scaled_lvs$sites,
  #            groups = predictors$treatments,
  #            draw = "polygon", border = FALSE,  col = c(col_control_120, col_pasture_120, col_sugarcane_120), kind = "sd", alpha = 50)

  points(scaled_lvs$sites[predictors$survey == "1" ,], bg = col_survey_1, pch = 21)
  points(scaled_lvs$sites[predictors$survey == "2" ,], bg = col_survey_2, pch = 21)
  points(scaled_lvs$sites[predictors$survey == "3" ,], bg = col_survey_3, pch = 21)
  points(scaled_lvs$sites[predictors$survey == "4" ,], bg = col_survey_4, pch = 21)


  centroid_1 <- colMeans(scaled_lvs$sites[predictors$survey == "1" ,])
  centroid_2 <- colMeans(scaled_lvs$sites[predictors$survey == "2" ,])
  centroid_3 <- colMeans(scaled_lvs$sites[predictors$survey == "3" ,])
  centroid_4 <- colMeans(scaled_lvs$sites[predictors$survey == "4" ,])

  #centroid_control_30 <- colMeans(scaled_lvs$sites[predictors$treatments == "control",])
  #centroid_pasture_30 <- colMeans(scaled_lvs$sites[predictors$treatments == "pasture",])
  #centroid_sugarcane_30 <- colMeans(scaled_lvs$sites[predictors$treatments == "sugar_cane",])


  #lines(x = c(centroid_control_30[1], centroid_sugarcane_30[1]),
  #      y = c(centroid_control_30[2], centroid_sugarcane_30[2]))

  #lines(x = c(centroid_pasture_30[1], centroid_sugarcane_30[1]),
  #      y = c(centroid_pasture_30[2], centroid_sugarcane_30[2]))



  for(i in 1:nrow(scaled_lvs$new_species)){
    points(x = scaled_lvs$new_species[i,1], y = scaled_lvs$new_species[i,2], cex = 4, pch = 21, bg = col[i])
    text(x = scaled_lvs$new_species[i,1], y = scaled_lvs$new_species[i,2], labels = substr(rownames(scaled_lvs$species)[i], 1, 3), cex = 0.9)
  }

  points(centroid_1[1], centroid_1[2], bg = col_survey_1, pch = 23, cex = 1.5)
  points(centroid_2[1], centroid_2[2], bg = col_survey_2, pch = 24, cex = 1.5)
  points(centroid_3[1], centroid_3[2], bg = col_survey_3, pch = 22, cex = 1.5)
  points(centroid_4[1], centroid_4[2], bg = col_survey_4, pch = 21, cex = 1.5)

  box()


par(mar = c(0,0,0,0),cex = 1.25)
plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(23, 24, 22, 21), legend = c("Centroid - 20 days", "Centroid - 40 days", "Centroid - 80 days", "Centroid - 160 days"), pt.bg	= c(col_survey_1, col_survey_2, col_survey_3, col_survey_4), bty = "n")

legend(x = 0, y = 50, pch = c(21), legend = c("Predatory Insects"), pt.bg	= c("lightsalmon1"), bty = "n", pt.cex	= 2.5, pt.lwd	= 1.5)
```


These are the coefficients Coefficients for each taxa
```{r, dpi=150, fig.width=6, fig.height=3, fig.align = 'center', warning=FALSE}

par(mar = c(4,8,2,.5), cex = 0.5, mfrow = c(1,3))

species_labels <- sub(pattern = ".", replacement = " ", x =names(effect_1_2), fixed = TRUE)

My_coefplot(mles = effect_1_2,
            lower = effect_1_2_lower,
            upper = effect_1_2_upper,
            species_labels = species_labels,  xlab = "Effect on abundance", main = "20 days vs 40 days",
            cex.axis = 1, cex.main = 1, font = 3, at.xaxis = c(-3,0,3,6,9))

My_coefplot(mles = effect_2_3,
            lower = effect_2_3_lower,
            upper = effect_2_3_upper,
            species_labels = species_labels,  xlab = "Effect on abundance", main = "40 days vs 80 days",
            cex.axis = 1, cex.main = 1, font = 3, break.axis = c(-3,-8), at.xaxis = c(-11, -9, -2, 0, 2, 4))

My_coefplot(mles = effect_3_4,
            lower = effect_3_4_lower,
            upper = effect_3_4_upper,
            species_labels = species_labels,  xlab = "Effect on abundance", main = "80 days vs 160 days",
            cex.axis = 1, cex.main = 1, font = 3)

```





## First Survey (20 day)

We always used a negative binomial distribution to model species abundances.

```{r}
SS1_predictors <- data.frame(treatments = treatments_SS1,
                             isolation = isolation_SS1)
```



Number of latent variables:
```{r, warning=FALSE}
n_latent_tab_SS1 <- run_multiple_lv(formula = ~ treatments * isolation,
                                   num.lv = c(0,1,2,3),
                                   y = com_predators_SS1, X = SS1_predictors,
                                   family = "negative.binomial",
                                   method = "VA",
                                   n.init = 10, seed = 11:20, starting.val = 0)

n_latent_tab_SS1$AICc_tab

```
It looks that zero latent variables is the way to go. This will repeat itself for the next cases.


Model selection of effects:
```{r, warning=FALSE, cache = TRUE}
model_predators_selection_SS1 <- run_multiple_gllvm(formulas = list(~ treatments,
                                   ~ isolation,
                                   ~ treatments + isolation,
                                   ~ treatments * isolation),
                   names = c("Treatments",
                             "Isolation",
                             "Isolation + Treatments",
                             "Isolation * Treatments"),
                   no_effect = TRUE,
                   num.lv = 0,
                   X = SS1_predictors,
                   y = com_predators_SS1,
                   family = "negative.binomial",
                   method = "VA",
                   n.init = 10, seed = 11:20, starting.val = 0)

model_predators_selection_SS1$AICc_tab
```
It seems there was no effect on community structure for the first survey.

Plots of ordinations
```{r, dpi=150, fig.width=9, fig.height=6, fig.align = 'center', warning=FALSE}

SS1_predictors <- data.frame(treatments = treatments_SS1,
                             isolation = isolation_SS1)

sum_com_predators_SS1 <- sum_com_SS1[,Trait_SS1_sum$trophic == "predator"]

col_SS1 <- rep("lightsalmon1", ncol(sum_com_predators_SS1))





fit_SS1_plot <- gllvm(sum_com_predators_SS1, #X = data.frame(ID = SS1_predictors[,1]),
                      formula = ~ 1,
                      family = "negative.binomial",
                      method = "VA",
                      #row.eff = ~ (1|ID),
                      n.init = 10, num.lv = 2, seed = 11:20, starting.val = "zero")


scaled_lvs <- get_scaled_lvs(fit_SS1_plot, alpha = 0.5)

set.seed(2)
scaled_lvs$species <- jitter(scaled_lvs$species, amount = 0.01)
set.seed(2)
scaled_lvs$sites <- jitter(scaled_lvs$sites, amount = 0.01)

scaled_lvs$new_species <- scaled_lvs$species/2

xmin <- min(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
xmax <- max(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
ymin <- min(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1
ymax <- max(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1


par(mar = c(4,4,1.25,.1), mfrow = c(2, 3))

plot_com_SS1_herb_treat_30()

plot_com_SS1_pred_treat_120()

plot_com_SS1_pred_treat_480()

par(mar = c(0,0,0,0),cex = 1.25)
plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(23, 23, 23), legend = c("Centroid - Control", "Centroid - Pasture", "Centroid - Sugarcane"), pt.bg	= c(col_control_30, col_pasture_30, col_sugarcane_30), bty = "n")

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21, 21, 21), legend = c("Ponds - Control", "Ponds - Pasture", "Ponds - Sugarcane"), pt.bg	= c(col_control_30, col_pasture_30, col_sugarcane_30), bty = "n", pt.cex	= 0.75)

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21), legend = c("Predatory Insects"), pt.bg	= c("lightsalmon1"), bty = "n", pt.cex	= 2.5, pt.lwd	= 1.5)


```

```{r, dpi=150, fig.width=9, fig.height=6, fig.align = 'center', warning=FALSE}

par(mar = c(4,4,1.25,.1), mfrow = c(2, 3))

plot_com_SS1_pred_iso_control()

plot_com_SS1_pred_iso_pasture()

plot_com_SS1_pred_iso_sugarcane()

par(mar = c(0,0,0,0),cex = 1.25)
plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(22, 21, 24), legend = c("Centroid - 30 m", "Centroid - 120 m", "Centroid - 480 m"), pt.bg	= c(col_control_30, col_control_120, col_control_480), bty = "n")

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(15, 16, 17), legend = c("Ponds - 30 m", "Ponds - 120 m", "Ponds - 480 m"), col	= c(col_control_30, col_control_120, col_control_480), bty = "n", pt.cex	= 0.75)

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21), legend = c("Predatory Insects"), pt.bg	= c("lightsalmon1"), bty = "n", pt.cex	= 2.5, pt.lwd	= 1.5)



```





## Second Survey (40 day)

```{r, warning=FALSE}
SS2_predictors <- data.frame(ID = ID_SS2_3_4,
                             treatments = treatments_SS2_3_4,
                             isolation = isolation_SS2_3_4,
                             isolation30_120480 = isolation30_120480_SS2_3_4,
                             isolation30120_480 = isolation30120_480_SS2_3_4,
                             treatments_contpast_sug = treatments_SS2_3_4_contpast_sug,
                             treatments_cont_pastsug = treatments_SS2_3_4_cont_pastsug,
                             treatments_contsug_past = treatments_SS2_3_4_contsug_past)
```


Number of latent variables:
```{r, cache = TRUE, warning=FALSE}
n_latent_tab_SS2 <- run_multiple_lv(num.lv = c(0,1,2,3),
                                formula = ~ treatments * isolation,
                                row.eff = ~ (1|ID),
                                y = com_predators_SS2, X = SS2_predictors,
                                family = "negative.binomial",
                                method = "VA",
                                n.init = 10, seed = 11:20)

n_latent_tab_SS2$AICc_tab

```
It looks that zero latent variables is the way to go.


Model selection of effects:
```{r, cache = TRUE, warning=FALSE}
model_predators_selection_SS2 <- run_multiple_gllvm(formulas = list(~ treatments,
                                                                                        ~ isolation,
                                                                                        ~ treatments + isolation,
                                                                                        ~ treatments * isolation),
                                                                        names = c("Treatments",
                                                                                  "Isolation",
                                                                                  "Isolation + Treatments",
                                                                                  "Isolation * Treatments"),
                                                                        no_effect = TRUE,
                                                                        num.lv = 0,
                                                                        X = SS2_predictors,
                                                                        X_row = data.frame(ID = ID_SS2_3_4),
                                                                        y = com_predators_SS2,
                                                                        row.eff = ~ (1|ID),
                                                                        family = "negative.binomial",
                                                                        method = "VA",
                                                                        n.init = 10, seed = 11:20)

model_predators_selection_SS2$AICc_tab
```
It seems there is an effect of treatments.

Lets look at pairwise differences:
```{r, cache = TRUE, warning=FALSE}
model_predators_selection_SS2_post_hoc_treatments <- run_multiple_gllvm(formulas = list(~ treatments,
                                                                    ~ treatments_contpast_sug,
                                                                    ~ treatments_cont_pastsug,
                                                                    ~ treatments_contsug_past),
                                                    names = c("control # pasture # sugarcane",
                                                              "(control = pasture) # sugarcane",
                                                              "control # (pasture = sugarcane)",
                                                              "(control = sugarcane) # pasture"),
                                                    no_effect = FALSE,
                                                    num.lv = 0,
                                                    X = SS2_predictors,
                                                    X_row = data.frame(ID = ID_SS2_3_4),
                                                    y = com_predators_SS2,
                                                    row.eff = ~ (1|ID),
                                                    family = "negative.binomial",
                                                    method = "VA",
                                                    n.init = 10, seed = 11:20)
model_predators_selection_SS2_post_hoc_treatments$AICc_tab
```
So, communities in the sugarcane treatment are different from the others.


Ploting it:
```{r, dpi=150, fig.width=9, fig.height=6, fig.align = 'center', warning=FALSE}

SS2_predictors <- data.frame(treatments = treatments_SS1,
                             isolation = isolation_SS1)

sum_com_predators_SS2 <- sum_com_SS2[,Trait_SS2_sum$trophic == "predator"]

col_SS2 <- rep("lightsalmon1", ncol(sum_com_predators_SS2))






fit_SS2_plot <- gllvm(sum_com_predators_SS2, #X = data.frame(ID = ID_SS2_3_4),
                      formula = ~ 1,
                      family = "negative.binomial",
                      method = "VA",
                      #row.eff = ~ (1|ID),
                      n.init = 10, num.lv = 2, seed = 11:20)


scaled_lvs <- get_scaled_lvs(fit_SS2_plot, alpha = 0.5)

set.seed(3)
scaled_lvs$species <- jitter(scaled_lvs$species, amount = 0.01)
set.seed(3)
scaled_lvs$sites <- jitter(scaled_lvs$sites, amount = 0.01)

scaled_lvs$new_species <- scaled_lvs$species/2


#LV1 <- tapply(scaled_lvs$sites[,1], INDEX = ID_SS2_3_4, median)
#LV2 <- tapply(scaled_lvs$sites[,2], INDEX = ID_SS2_3_4, median)

#scaled_lvs$sites <- data.frame(LV1,LV2)



xmin <- min(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
xmax <- max(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
ymin <- min(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1
ymax <- max(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1


par(mar = c(4,4,1.25,.1), mfrow = c(2, 3))

plot_com_SS2_pred_treat_30()

plot_com_SS2_pred_treat_120()

plot_com_SS2_pred_treat_480()

par(mar = c(0,0,0,0),cex = 1.25)
plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(23, 23, 23), legend = c("Centroid - Control", "Centroid - Pasture", "Centroid - Sugarcane"), pt.bg	= c(col_control_30, col_pasture_30, col_sugarcane_30), bty = "n")

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21, 21, 21), legend = c("Ponds - Control", "Ponds - Pasture", "Ponds - Sugarcane"), pt.bg	= c(col_control_30, col_pasture_30, col_sugarcane_30), bty = "n", pt.cex	= 0.75)

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21), legend = c("Predatory Insects"), pt.bg	= c("lightsalmon1"), bty = "n", pt.cex	= 2.5, pt.lwd	= 1.5)


```





These are the coefficients Coefficients for the difference of sugarcane communities from the others.
```{r, dpi=150, fig.width=6, fig.height=3, fig.align = 'center', warning=FALSE}

par(mar = c(4,8,2,.5), cex = 0.5, mfrow = c(1,3))

species_labels_SS2 <- sub(pattern = ".", replacement = " ", x =names(effect_SS2_control_sugar_cane), fixed = TRUE)

My_coefplot(mles = effect_SS2_control_sugar_cane,
            lower = effect_SS2_control_sugar_cane_lower,
            upper = effect_SS2_control_sugar_cane_upper,
            species_labels = species_labels_SS2,  xlab = "Effect on abundance", main = "Savanna/Pasture vs Sugarcane",
            cex.axis = 1, cex.main = 1, font = 3, at.xaxis = c(2,0,-2,-4, -14, -16),break.axis = c(-6,-12))


```


Ordinations focusing on isolation
```{r, dpi=150, fig.width=9, fig.height=6, fig.align = 'center', warning=FALSE}

par(mar = c(4,4,1.25,.1), mfrow = c(2, 3))

plot_com_SS2_pred_iso_control()

plot_com_SS2_pred_iso_pasture()

plot_com_SS2_pred_iso_sugarcane()

par(mar = c(0,0,0,0),cex = 1.25)
plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(22, 21, 24), legend = c("Centroid - 30 m", "Centroid - 120 m", "Centroid - 480 m"), pt.bg	= c(col_control_30, col_control_120, col_control_480), bty = "n")

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(15, 16, 17), legend = c("Ponds - 30 m", "Ponds - 120 m", "Ponds - 480 m"), col	= c(col_control_30, col_control_120, col_control_480), bty = "n", pt.cex	= 0.75)

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21), legend = c("Predatory Insects"), pt.bg	= c("lightsalmon1"), bty = "n", pt.cex	= 2.5, pt.lwd	= 1.5)


```



## Third Survey (80 day)


```{r, warning=FALSE}
SS3_predictors <- data.frame(ID = ID_SS2_3_4,
                             treatments = treatments_SS2_3_4,
                             isolation = isolation_SS2_3_4,
                             isolation30_120480 = isolation30_120480_SS2_3_4,
                             isolation30120_480 = isolation30120_480_SS2_3_4,
                             treatments_contpast_sug = treatments_SS2_3_4_contpast_sug,
                             treatments_cont_pastsug = treatments_SS2_3_4_cont_pastsug,
                             treatments_contsug_past = treatments_SS2_3_4_contsug_past)
```


Number of latent variables:
```{r, cache = TRUE, warning=FALSE}
n_latent_tab_SS3 <- run_multiple_lv(num.lv = c(0,1,2,3),
                                    formula = ~ treatments * isolation,
                                    row.eff = ~ (1|ID),
                                    y = com_predators_SS3, X = SS3_predictors,
                                    family = "negative.binomial",
                                    method = "VA",
                                    n.init = 10, seed = 11:20)

n_latent_tab_SS3$AICc_tab

```
It looks that zero latent variables is the way to go.


Model selection of effects:
```{r, cache = TRUE, warning=FALSE}
model_predators_selection_SS3 <- run_multiple_gllvm(formulas = list(~ treatments,
                                                                    ~ isolation,
                                                                    ~ treatments + isolation,
                                                                    ~ treatments * isolation),
                                                    names = c("Treatments",
                                                              "Isolation",
                                                              "Isolation + Treatments",
                                                              "Isolation * Treatments"),
                                                    no_effect = TRUE,
                                                    num.lv = 0,
                                                    X = SS3_predictors,
                                                    X_row = data.frame(ID = ID_SS2_3_4),
                                                    y = com_predators_SS3,
                                                    row.eff = ~ (1|ID),
                                                    family = "negative.binomial",
                                                    method = "VA",
                                                    n.init = 10, seed = 11:20)

model_predators_selection_SS3$AICc_tab
```
It seems like there are main effects of treatments and isolation.

Lets look at pairwise differences of treatments:
```{r, cache = TRUE, warning=FALSE}
model_predators_selection_SS3_post_hoc_treatments <- run_multiple_gllvm(formulas = list(~ treatments + isolation,
                                                                                        ~ treatments_contpast_sug + isolation,
                                                                                        ~ treatments_cont_pastsug + isolation,
                                                                                        ~ treatments_contsug_past + isolation),
                                                                        names = c("control # pasture # sugarcane",
                                                                                  "(control = pasture) # sugarcane",
                                                                                  "control # (pasture = sugarcane)",
                                                                                  "(control = sugarcane) # pasture"),
                                                                        no_effect = FALSE,
                                                                        num.lv = 0,
                                                                        X = SS3_predictors,
                                                                        X_row = data.frame(ID = ID_SS2_3_4),
                                                                        y = com_predators_SS3,
                                                                        row.eff = ~ (1|ID),
                                                                        family = "negative.binomial",
                                                                        method = "VA",
                                                                        n.init = 10, seed = 11:20)
model_predators_selection_SS3_post_hoc_treatments
```
It seems that all treatments are different from each other.

Now, pairwise differences of isolation:
```{r, warning=FALSE}
model_predators_selection_SS3_post_hoc_isolation <- run_multiple_gllvm(formulas = list(~ isolation + treatments,
                                                                                        ~ isolation30120_480 + treatments,
                                                                                        ~ isolation30_120480 + treatments),
                                                                        names = c("30 # 120 # 480",
                                                                                  "(30 = 120) # 480",
                                                                                  "30 # (120 = 480)"),
                                                                        no_effect = FALSE,
                                                                        num.lv = 0,
                                                                        X = SS3_predictors,
                                                                        X_row = data.frame(ID = ID_SS2_3_4),
                                                                        y = com_predators_SS3,
                                                                        row.eff = ~ (1|ID),
                                                                        family = "negative.binomial",
                                                                        method = "VA",
                                                                        n.init = 10, seed = 11:20)
model_predators_selection_SS3_post_hoc_isolation$AICc_tab
```
480m is different from 30 and 120m.


Ploting it:
```{r, dpi=150, fig.width=9, fig.height=6, fig.align = 'center', warning=FALSE}
SS3_predictors <- data.frame(treatments = treatments_SS1,
                             isolation = isolation_SS1)

sum_com_predators_SS3 <- sum_com_SS3[,Trait_SS3_sum$trophic == "predator"]

col_SS3 <- rep("lightsalmon1", ncol(sum_com_predators_SS3))


fit_SS3_plot <- gllvm(sum_com_predators_SS3, #X = data.frame(ID = ID_SS2_3_4),
                      formula = ~ 1,
                      family = "negative.binomial",
                      method = "VA",
                      #row.eff = ~ (1|ID),
                      n.init = 10, num.lv = 2, seed = 11:20)


scaled_lvs <- get_scaled_lvs(fit_SS3_plot, alpha = 0.5)

set.seed(4)
scaled_lvs$species <- jitter(scaled_lvs$species, amount = 0.01)
set.seed(3)
scaled_lvs$sites <- jitter(scaled_lvs$sites, amount = 0.01)

scaled_lvs$new_species <- scaled_lvs$species/3


#LV1 <- tapply(scaled_lvs$sites[,1], INDEX = ID_SS2_3_4, median)
#LV2 <- tapply(scaled_lvs$sites[,2], INDEX = ID_SS2_3_4, median)

#scaled_lvs$sites <- data.frame(LV1,LV2)



xmin <- min(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
xmax <- max(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
ymin <- min(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1
ymax <- max(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1


par(mar = c(4,4,1.25,.1), mfrow = c(2, 3))

plot_com_SS3_pred_treat_30()

plot_com_SS3_pred_treat_120()

plot_com_SS3_pred_treat_480()

par(mar = c(0,0,0,0),cex = 1.25)
plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(23, 23, 23), legend = c("Centroid - Control", "Centroid - Pasture", "Centroid - Sugarcane"), pt.bg	= c(col_control_30, col_pasture_30, col_sugarcane_30), bty = "n")

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21, 21, 21), legend = c("Ponds - Control", "Ponds - Pasture", "Ponds - Sugarcane"), pt.bg	= c(col_control_30, col_pasture_30, col_sugarcane_30), bty = "n", pt.cex	= 0.75)

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21), legend = c("Predatory Insects"), pt.bg	= c("lightsalmon1"), bty = "n", pt.cex	= 2.5, pt.lwd	= 1.5)



```


Now the coefficients
```{r, dpi=150, fig.width=6, fig.height=3, fig.align = 'center', warning=FALSE}

par(mar = c(4,8,2,.5), cex = 0.5, mfrow = c(1,3))

species_labels_SS3 <- sub(pattern = ".", replacement = " ", x =names(effect_SS3_control_sugar_cane), fixed = TRUE)

My_coefplot(mles = effect_SS3_control_pasture,
            lower = effect_SS3_control_pasture_lower,
            upper = effect_SS3_control_pasture_upper,
            species_labels = species_labels_SS3,  xlab = "Effect on abundance", main = "Savanna vs Pasture",
            cex.axis = 1, cex.main = 1, font = 3, at.xaxis = c(6,4,2,0,-2,-4, -450, -476),break.axis = c(-6,-474))


My_coefplot(mles = effect_SS3_control_sugar_cane,
            lower = effect_SS3_control_sugar_cane_lower,
            upper = effect_SS3_control_sugar_cane_upper,
            species_labels = species_labels_SS3,  xlab = "Effect on abundance", main = "Savanna vs Sugarcane",
            cex.axis = 1, cex.main = 1, font = 3)#, at.xaxis = c(6, 4,2,0,-2,-4, -450, -476),break.axis = c(-6,-474))


My_coefplot(mles = effect_SS3_pasture_sugar_cane,
            lower = effect_SS3_pasture_sugar_cane_lower,
            upper = effect_SS3_pasture_sugar_cane_upper,
            species_labels = species_labels_SS3,  xlab = "Effect on abundance", main = "Pasture vs Sugarcane",
            cex.axis = 1, cex.main = 1, font = 3)#, at.xaxis = c(6, 4,2,0,-2,-4, -450, -476),break.axis = c(-6,-474))




```




```{r, dpi=150, fig.width=9, fig.height=6, fig.align = 'center', warning=FALSE}


par(mar = c(4,4,1.25,.1), mfrow = c(2, 3))

plot_com_SS3_pred_iso_control()

plot_com_SS3_pred_iso_pasture()

plot_com_SS3_pred_iso_sugarcane()

par(mar = c(0,0,0,0),cex = 1.25)
plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(22, 21, 24), legend = c("Centroid - 30 m", "Centroid - 120 m", "Centroid - 480 m"), pt.bg	= c(col_control_30, col_control_120, col_control_480), bty = "n")

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(15, 16, 17), legend = c("Ponds - 30 m", "Ponds - 120 m", "Ponds - 480 m"), col	= c(col_control_30, col_control_120, col_control_480), bty = "n", pt.cex	= 0.75)

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21), legend = c("Predatory Insects"), pt.bg	= c("lightsalmon1"), bty = "n", pt.cex	= 2.5, pt.lwd	= 1.5)


```

```{r, dpi=150, fig.width=6, fig.height=3, fig.align = 'center', warning=FALSE}

par(mar = c(4,8,2,.5), cex = 0.5, mfrow = c(1,3))


My_coefplot(mles = effect_SS3_30_120_480,
            lower = effect_SS3_30_120_480_lower,
            upper = effect_SS3_30_120_480_upper,
            species_labels = species_labels_SS3,  xlab = "Effect on abundance", main = "30/120 vs 480",
            cex.axis = 1, cex.main = 1, font = 3)#, at.xaxis = c(6, 4,2,0,-2,-4, -450, -476),break.axis = c(-6,-474))


```




## Fourth Survey (160 day)

```{r, warning=FALSE}
SS4_predictors <- data.frame(ID = ID_SS2_3_4,
                             treatments = treatments_SS2_3_4,
                             isolation = isolation_SS2_3_4,
                             isolation30_120480 = isolation30_120480_SS2_3_4,
                             isolation30120_480 = isolation30120_480_SS2_3_4,
                             treatments_contpast_sug = treatments_SS2_3_4_contpast_sug,
                             treatments_cont_pastsug = treatments_SS2_3_4_cont_pastsug,
                             treatments_contsug_past = treatments_SS2_3_4_contsug_past)
```


Number of latent variables:
```{r, cache = TRUE, warning=FALSE}
n_latent_tab_SS4 <- run_multiple_lv(num.lv = c(0,1,2,3),
                                    formula = ~ treatments * isolation,
                                    row.eff = ~ (1|ID),
                                    y = com_predators_SS4, X = SS4_predictors,
                                    family = "negative.binomial",
                                    method = "VA",
                                    n.init = 10, seed = 11:20)

n_latent_tab_SS4$AICc_tab

```
It looks that zero latent variables is the way to go.


Model selection of effects:
```{r, cache = TRUE, warning=FALSE}
model_predators_selection_SS4 <- run_multiple_gllvm(formulas = list(~ treatments,
                                                                    ~ isolation,
                                                                    ~ treatments + isolation,
                                                                    ~ treatments * isolation),
                                                    names = c("Treatments",
                                                              "Isolation",
                                                              "Isolation + Treatments",
                                                              "Isolation * Treatments"),
                                                    no_effect = TRUE,
                                                    num.lv = 0,
                                                    X = SS4_predictors,
                                                    X_row = data.frame(ID = ID_SS2_3_4),
                                                    y = com_predators_SS4,
                                                    row.eff = ~ (1|ID),
                                                    family = "negative.binomial",
                                                    method = "VA",
                                                    n.init = 10, seed = 11:20)

model_predators_selection_SS4$AICc_tab
```
It seems like there are main effects of treatments and isolation.

Lets look at pairwise differences of treatments:
```{r, cache = TRUE, warning=FALSE}
model_predators_selection_SS4_post_hoc_treatments <- run_multiple_gllvm(formulas = list(~ treatments + isolation,
                                                                                        ~ treatments_contpast_sug + isolation,
                                                                                        ~ treatments_cont_pastsug + isolation,
                                                                                        ~ treatments_contsug_past + isolation),
                                                                        names = c("control # pasture # sugarcane",
                                                                                  "(control = pasture) # sugarcane",
                                                                                  "control # (pasture = sugarcane)",
                                                                                  "(control = sugarcane) # pasture"),
                                                                        no_effect = FALSE,
                                                                        num.lv = 0,
                                                                        X = SS4_predictors,
                                                                        X_row = data.frame(ID = ID_SS2_3_4),
                                                                        y = com_predators_SS4,
                                                                        row.eff = ~ (1|ID),
                                                                        family = "negative.binomial",
                                                                        method = "VA",
                                                                        n.init = 10, seed = 11:20)
model_predators_selection_SS4_post_hoc_treatments$AICc_tab
```
It seems that we only have enough evidence so say that sugarcane communities are different from control.

Now, pairwise differences of isolation:
```{r, warning=FALSE}
model_predators_selection_SS4_post_hoc_isolation <- run_multiple_gllvm(formulas = list(~ isolation + treatments_cont_pastsug,
                                                                                       ~ isolation30120_480 + treatments_cont_pastsug,
                                                                                       ~ isolation30_120480 + treatments_cont_pastsug),
                                                                       names = c("30 # 120 # 480",
                                                                                 "(30 = 120) # 480",
                                                                                 "30 # (120 = 480)"),
                                                                       no_effect = FALSE,
                                                                       num.lv = 0,
                                                                       X = SS4_predictors,
                                                                       X_row = data.frame(ID = ID_SS2_3_4),
                                                                       y = com_predators_SS4,
                                                                       row.eff = ~ (1|ID),
                                                                       family = "negative.binomial",
                                                                       method = "VA",
                                                                       n.init = 10, seed = 11:20)
model_predators_selection_SS4_post_hoc_isolation$AICc_tab
```
All levels are different.


Ploting it:
```{r, dpi=150, fig.width=9, fig.height=6, fig.align = 'center', warning=FALSE}
SS4_predictors <- data.frame(treatments = treatments_SS1,
                             isolation = isolation_SS1)

sum_com_predators_SS4 <- sum_com_SS4[,Trait_SS4_sum$trophic == "predator"]

col_SS4 <- rep("lightsalmon1", ncol(sum_com_predators_SS4))






fit_SS4_plot <- gllvm(sum_com_predators_SS4, #X = data.frame(ID = ID_SS2_3_4),
                      formula = ~ 1,
                      family = "negative.binomial",
                      method = "VA",
                      #row.eff = "random",
                      n.init = 10, num.lv = 2, seed = 11:20)


scaled_lvs <- get_scaled_lvs(fit_SS4_plot, alpha = 0.5)

set.seed(3)
scaled_lvs$species <- jitter(scaled_lvs$species, amount = 0.01)
set.seed(3)
scaled_lvs$sites <- jitter(scaled_lvs$sites, amount = 0.01)

scaled_lvs$new_species <- scaled_lvs$species/3


#LV1 <- tapply(scaled_lvs$sites[,1], INDEX = ID_SS2_3_4, median)
#LV2 <- tapply(scaled_lvs$sites[,2], INDEX = ID_SS2_3_4, median)

#scaled_lvs$sites <- data.frame(LV1,LV2)



xmin <- min(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
xmax <- max(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
ymin <- min(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1
ymax <- max(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1



par(mar = c(4,4,1.25,.1), mfrow = c(2, 3))

plot_com_SS4_pred_treat_30()

plot_com_SS4_pred_treat_120()

plot_com_SS4_pred_treat_480()

par(mar = c(0,0,0,0),cex = 1.25)
plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(23, 23, 23), legend = c("Centroid - Control", "Centroid - Pasture", "Centroid - Sugarcane"), pt.bg	= c(col_control_30, col_pasture_30, col_sugarcane_30), bty = "n")

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21, 21, 21), legend = c("Ponds - Control", "Ponds - Pasture", "Ponds - Sugarcane"), pt.bg	= c(col_control_30, col_pasture_30, col_sugarcane_30), bty = "n", pt.cex	= 0.75)

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21), legend = c("Predatory Insects"), pt.bg	= c("lightsalmon1"), bty = "n", pt.cex	= 2.5, pt.lwd	= 1.5)




```

```{r, dpi=150, fig.width=6, fig.height=3, fig.align = 'center', warning=FALSE}
par(mar = c(4,8,2,.5), cex = 0.5, mfrow = c(1,3))

species_labels_SS4 <- sub(pattern = ".", replacement = " ", x =names(effect_SS4_control_sugar_cane), fixed = TRUE)

My_coefplot(mles = effect_SS4_control_sugar_cane,
            lower = effect_SS4_control_sugar_cane_lower,
            upper = effect_SS4_control_sugar_cane_upper,
            species_labels = species_labels_SS4,  xlab = "Effect on abundance", main = "Savanna vs Sugarcane",
            cex.axis = 1, cex.main = 1, font = 3)#, at.xaxis = c(6, 4,2,0,-2,-4, -450, -476),break.axis = c(-6,-474))


```


```{r, dpi=150, fig.width=9, fig.height=6, fig.align = 'center', warning=FALSE}


par(mar = c(4,4,1.25,.1), mfrow = c(2, 3))

plot_com_SS4_pred_iso_control()

plot_com_SS4_pred_iso_pasture()

plot_com_SS4_pred_iso_sugarcane()

par(mar = c(0,0,0,0),cex = 1.25)
plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(22, 21, 24), legend = c("Centroid - 30 m", "Centroid - 120 m", "Centroid - 480 m"), pt.bg	= c(col_control_30, col_control_120, col_control_480), bty = "n")

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(15, 16, 17), legend = c("Ponds - 30 m", "Ponds - 120 m", "Ponds - 480 m"), col	= c(col_control_30, col_control_120, col_control_480), bty = "n", pt.cex	= 0.75)

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21), legend = c("Predatory Insects"), pt.bg	= c("lightsalmon1"), bty = "n", pt.cex	= 2.5, pt.lwd	= 1.5)


```

```{r, dpi=150, fig.width=6, fig.height=3, fig.align = 'center', warning=FALSE}
par(mar = c(4,8,2,.5), cex = 0.5, mfrow = c(1,3))

My_coefplot(mles = effect_SS4_30_120,
            lower = effect_SS4_30_120_lower,
            upper = effect_SS4_30_120_upper,
            species_labels = species_labels_SS4,  xlab = "Effect on abundance", main = "30 vs 120",
            cex.axis = 1, cex.main = 1, font = 3)#, at.xaxis = c(6, 4,2,0,-2,-4, -450, -476),break.axis = c(-6,-474))


My_coefplot(mles = effect_SS4_30_480,
            lower = effect_SS4_30_480_lower,
            upper = effect_SS4_30_480_upper,
            species_labels = species_labels_SS4,  xlab = "Effect on abundance", main = "30 vs 480",
            cex.axis = 1, cex.main = 1, font = 3)#, at.xaxis = c(6, 4,2,0,-2,-4, -450, -476),break.axis = c(-6,-474))


My_coefplot(mles = effect_SS4_120_480,
            lower = effect_SS4_120_480_lower,
            upper = effect_SS4_120_480_upper,
            species_labels = species_labels_SS4,  xlab = "Effect on abundance", main = "120 vs 480",
            cex.axis = 1, cex.main = 1, font = 3)#, at.xaxis = c(6, 4,2,0,-2,-4, -450, -476),break.axis = c(-6,-474))



```

