---
title: "Community Structure - Herbivore and Detritivores"
author: "Rodolfo Pelinson"
date: "27/12/2022"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r echo = TRUE, message=FALSE, warning=FALSE}
library(vegan)
library(gllvm)
```

```{r include = FALSE}
setwd("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/IsolationAgrochemicals")
source("Auxiliary scripts/Loading_data.R")
source("Auxiliary scripts/Ordination_plots.R")

```


Before anything, here are three functions that will automate most of the model selection procedures that we will be doing. The script would be gigantic without them.

This first one is just to make a model selection table based on AICc for gllvm models. All functions rely on the gllvm function from the `gllvm` version 1.3.1 (it may need adjustments for other versions).
```{r}
setwd("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/IsolationAgrochemicals")
source("Auxiliary scripts/gllvm_AICc_tab.R")
```

This one is to run multiple gllvms with different number of latent variables and perform model selection. Its useful to find the ideal number of latent variables necessary to accurately account for correlations (dependencies) in species co-occurrences not caused by our treatments.
```{r}
setwd("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/IsolationAgrochemicals")
source("Auxiliary scripts/run_multiple_lv.R")
```

This is to automate running multiple gllvms and perform model selection

```{r}
setwd("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/IsolationAgrochemicals")
source("Auxiliary scripts/run_multiple_gllvm.R")
```


This is for getting scaled latent variables for plotting model based ordinations. I took most of code from the plotting functions from the `gllvm` package.
```{r}
setwd("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/IsolationAgrochemicals")
source("Auxiliary scripts/get_scaled_lvs.R")
```



# Herbivores and Detritivores

Lets make tables with only herbivore and insectivores. Note that here we excludes species that occur in less than 4 samples in each survey because are less informative to community patterns and complicate parameter estimation.

```{r, warning=FALSE}

#cheking if the order of row in Trait_og and columns in com_orig match

data.frame(com = colnames(com), trait = Trait$genus)

com_herb_det <- com[,Trait$trophic == "consumer"]
com_herb_det_SS1 <- com_SS1[,Trait_SS1$trophic == "consumer"]
com_herb_det_SS2 <- com_SS2[,Trait_SS2$trophic == "consumer"]
com_herb_det_SS3 <- com_SS3[,Trait_SS3$trophic == "consumer"]
com_herb_det_SS4 <- com_SS4[,Trait_SS4$trophic == "consumer"]
```

## All surveys

We always used a negative binomial distribution to model species abundances.


```{r}
predictors <- data.frame(ID = ID,
                         treatments = treatments_all,
                         isolation = isolation_all,
                         survey = SS)
```


Number of latent variables:
```{r, warning=FALSE, chache = TRUE}
n_latent_tab <- run_multiple_lv(formula = ~ treatments * isolation * survey,
                                    num.lv = c(0,1,2,3),
                                    row.eff = ~ (1|ID),
                                    y = com_herb_det, X = predictors,
                                    family = "negative.binomial",
                                    method = "VA",
                                    n.init = 10, seed = 1:10)

n_latent_tab$AICc_tab

```
It looks that zero latent variables is the way to go. This will repeat itself for the next cases.


Model selection of effects:
```{r, warning=FALSE, cache = TRUE}
model_herb_det_selection <- run_multiple_gllvm(formulas = list(    ~ survey,
                                                                    ~ treatments * isolation,
                                                                    ~ survey + (treatments * isolation),
                                                                    ~ survey * (treatments * isolation)),
                                                    names = c("Survey",
                                                              "Isolation * Treatments",
                                                              "Survey + (Isolation * Treatments)",
                                                              "Survey * (Isolation * Treatments)"),
                                                    no_effect = TRUE,
                                                    num.lv = 0,
                                                    row.eff = ~ (1|ID),
                                                    X_row = data.frame(ID = ID),
                                                    X = predictors,
                                                    y = com_herb_det,
                                                    family = "negative.binomial",
                                                    method = "VA",
                                                    n.init = 10, seed = 1:10)

model_herb_det_selection$AICc_tab
```
It seems that the effect of treatments is different in each survey.




## First Survey (20 day)


```{r}
SS1_predictors <- data.frame(treatments = treatments_SS1,
                             isolation = isolation_SS1,
                             isolation30120_480,
                             isolation30_120480)
```



Number of latent variables:
```{r, warning=FALSE}
n_latent_tab_SS1 <- run_multiple_lv(formula = ~ treatments * isolation,
                                    num.lv = c(0,1,2,3),
                                    y = com_herb_det_SS1, X = SS1_predictors,
                                    family = "negative.binomial",
                                    method = "VA",
                                    n.init = 10, seed = 1:10, starting.val = 0)

n_latent_tab_SS1$AICc_tab

```
It looks that zero latent variables is the way to go. This will repeat itself for the next cases.


Model selection of effects:
```{r, warning=FALSE}
model_herb_det_selection_SS1 <- run_multiple_gllvm(formulas = list(~ treatments,
                                                                    ~ isolation,
                                                                    ~ treatments + isolation,
                                                                    ~ treatments * isolation),
                                                    names = c("Treatments",
                                                              "Isolation",
                                                              "Isolation + Treatments",
                                                              "Isolation * Treatments"),
                                                    no_effect = TRUE,
                                                    num.lv = 0,
                                                    X = SS1_predictors,
                                                    y = com_herb_det_SS1,
                                                    family = "negative.binomial",
                                                    method = "VA",
                                                    n.init = 10, seed = 1:10, starting.val = 0)

model_herb_det_selection_SS1$AICc_tab
```
It seems that isolation is important.

Let's go for pairwise differences:
```{r, warning=FALSE}
model_herb_det_selection_SS1_post_hoc_isolation <- run_multiple_gllvm(formulas = list(~ isolation,
                                                                                      ~ isolation30120_480,
                                                                                      ~ isolation30_120480),
                                                                      names = c("30 # 120 # 480",
                                                                                "(30 = 120) # 480",
                                                                                "30 # (120 = 480)"),
                                                                      no_effect = FALSE,
                                                                      num.lv = 0,
                                                                      X = SS1_predictors,
                                                                      y = com_herb_det_SS1,
                                                                      family = "negative.binomial",
                                                                      method = "VA",
                                                                      n.init = 10, seed = 1:10)

model_herb_det_selection_SS1_post_hoc_isolation$AICc_tab

```
30m is different from 120 and 480m.


The code for plotting the ordinations is again pretty extensive, I will then only show the first one as an example e call the others from functions sourced from the 'Auxiliary scripts" folder.

```{r, dpi=150, fig.width=9, fig.height=6, fig.align = 'center', warning=FALSE}

SS1_predictors <- data.frame(treatments = treatments_SS1,
                             isolation = isolation_SS1)

sum_com_herb_det_SS1 <- sum_com_SS1[,Trait_SS1_sum$trophic == "consumer"]

col_SS1 <- rep("darkolivegreen3", ncol(sum_com_herb_det_SS1))
col_SS1[Trait_SS1$trait[Trait_SS1$trophic == "consumer"] == "insect_consumer" ] <- "cyan3"


fit_SS1_plot <- gllvm(sum_com_herb_det_SS1, 
                      formula = ~ 1,
                      family = "negative.binomial",
                      method = "VA",
                      n.init = 10, num.lv = 2, seed = 11:20, starting.val = "zero")


scaled_lvs <- get_scaled_lvs(fit_SS1_plot, alpha = 0.5)

#It was necessary to add a jitter to improve vizualization
set.seed(3)
scaled_lvs$species <- jitter(scaled_lvs$species, amount = 0.01)
set.seed(3)
scaled_lvs$sites <- jitter(scaled_lvs$sites, amount = 0.01)

scaled_lvs$new_species <- scaled_lvs$species/3

xmin <- min(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
xmax <- max(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
ymin <- min(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1
ymax <- max(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1


par(mar = c(4,4,1.25,.1), mfrow = c(2, 3))
plot(NA,xlim = c(xmin, xmax), ylim = c(ymin, ymax), ylab = "LV2", xlab = "LV1", axes = F)
axis(1 , gap.axis = -10)
axis(2 , gap.axis = -10)
abline(h=0,v=0, lty =2)

ordiellipse(scaled_lvs$sites[SS1_predictors$isolation == "30",],
            groups = SS1_predictors$treatments[SS1_predictors$isolation == "30"],
            draw = "polygon", border = FALSE,  col = c(col_control_120, col_pasture_120, col_sugarcane_120), kind = "sd", alpha = 50)

#ordiellipse(scaled_lvs$sites,
#            groups = SS1_predictors$treatments,
#            draw = "polygon", border = FALSE,  col = c(col_control_120, col_pasture_120, col_sugarcane_120), kind = "sd", alpha = 50)

points(scaled_lvs$sites[SS1_predictors$treatments == "control" & SS1_predictors$isolation == "30",], bg = col_control_30, pch = 21)
points(scaled_lvs$sites[SS1_predictors$treatments == "pasture" & SS1_predictors$isolation == "30",], bg = col_pasture_30, pch = 21)
points(scaled_lvs$sites[SS1_predictors$treatments == "sugar_cane" & SS1_predictors$isolation == "30",], bg = col_sugarcane_30, pch = 21)


centroid_control_30 <- colMeans(scaled_lvs$sites[SS1_predictors$treatments == "control" & SS1_predictors$isolation == "30",])
centroid_pasture_30 <- colMeans(scaled_lvs$sites[SS1_predictors$treatments == "pasture" & SS1_predictors$isolation == "30",])
centroid_sugarcane_30 <- colMeans(scaled_lvs$sites[SS1_predictors$treatments == "sugar_cane" & SS1_predictors$isolation == "30",])

#centroid_control_30 <- colMeans(scaled_lvs$sites[SS1_predictors$treatments == "control",])
#centroid_pasture_30 <- colMeans(scaled_lvs$sites[SS1_predictors$treatments == "pasture",])
#centroid_sugarcane_30 <- colMeans(scaled_lvs$sites[SS1_predictors$treatments == "sugar_cane",])

for(i in 1:nrow(scaled_lvs$new_species)){
  points(x = scaled_lvs$new_species[i,1], y = scaled_lvs$new_species[i,2], cex = 4, pch = 21, bg = col_SS1[i])
  text(x = scaled_lvs$new_species[i,1], y = scaled_lvs$new_species[i,2], labels = substr(rownames(scaled_lvs$species)[i], 1, 3), cex = 0.9)
}

points(centroid_control_30[1], centroid_control_30[2], bg = col_control_30, pch = 23, cex = 1.5)
points(centroid_pasture_30[1], centroid_pasture_30[2], bg = col_pasture_30, pch = 23, cex = 1.5)
points(centroid_sugarcane_30[1], centroid_sugarcane_30[2], bg = col_sugarcane_30, pch = 23, cex = 1.5)

lines(x = c(centroid_control_30[1], centroid_pasture_30[1]),
      y = c(centroid_control_30[2], centroid_pasture_30[2]))

lines(x = c(centroid_control_30[1], centroid_sugarcane_30[1]),
      y = c(centroid_control_30[2], centroid_sugarcane_30[2]))

lines(x = c(centroid_pasture_30[1], centroid_sugarcane_30[1]),
      y = c(centroid_pasture_30[2], centroid_sugarcane_30[2]))

box()

title(main = "30 m", adj = 1, line = 0.25)

plot_com_SS1_herb_treat_120()

plot_com_SS1_herb_treat_480()

par(mar = c(0,0,0,0),cex = 1.25)
plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(23, 23, 23), legend = c("Centroid - Control", "Centroid - Pasture", "Centroid - Sugarcane"), pt.bg	= c(col_control_30, col_pasture_30, col_sugarcane_30), bty = "n")

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21, 21, 21), legend = c("Ponds - Control", "Ponds - Pasture", "Ponds - Sugarcane"), pt.bg	= c(col_control_30, col_pasture_30, col_sugarcane_30), bty = "n", pt.cex	= 0.75)

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21, 21), legend = c("Insects", "Amphibians"), pt.bg	= c("cyan3","darkolivegreen3"), bty = "n", pt.cex	= 2.5, pt.lwd	= 1.5)

```

Now the same plots but for isolation:
```{r, dpi=150, fig.width=9, fig.height=6, fig.align = 'center', warning=FALSE}
par(mar = c(4,4,1.25,.1), mfrow = c(2, 3))

plot_com_SS1_herb_iso_control()

plot_com_SS1_herb_iso_pasture()

plot_com_SS1_herb_iso_sugarcane()

par(mar = c(0,0,0,0),cex = 1.25)
plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(22, 21, 24), legend = c("Centroid - 30 m", "Centroid - 120 m", "Centroid - 480 m"), pt.bg	= c(col_control_30, col_control_120, col_control_480), bty = "n")

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(15, 16, 17), legend = c("Ponds - 30 m", "Ponds - 120 m", "Ponds - 480 m"), col	= c(col_control_30, col_control_120, col_control_480), bty = "n", pt.cex	= 0.75)

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21, 21), legend = c("Insects", "Amphibians"), pt.bg	= c("cyan3","darkolivegreen3"), bty = "n", pt.cex	= 2.5, pt.lwd	= 1.5)

```


Ploting species coefficients and their confidence intervals based on the effects identified in the analysis. The script for extracting these coefficients and the function for plotting is rather extensive, thus I will source the code on a script in the Auxiliary Scripts folder. You can check the original code there.

```{r, warning=FALSE}
setwd("C:/Users/rodol/OneDrive/Trabalho/Papers/Analysis/IsolationAgrochemicals")
source("Auxiliary scripts/coefficients for herb_det.R")
source("Auxiliary scripts/My_coefplot.R")
```


These are the coefficients Coefficients for the difference of communities at 30m VS those at 120 and 480m:
```{r, dpi=150, fig.width=6, fig.height=3, fig.align = 'center', warning=FALSE}

par(mar = c(4,8,2,.5), cex = 0.5, mfrow = c(1,3))

species_labels_SS1 <- sub(pattern = ".", replacement = " ", x =names(effect_SS1_30480), fixed = TRUE)
species_labels_SS1 <- sub(pattern = "Physalaemos", replacement = "P.", x =species_labels_SS1, fixed = TRUE)


My_coefplot(effect_SS1_30480,
            effect_SS1_30480_lower,
            effect_SS1_30480_upper,
            species_labels = species_labels_SS1,  xlab = "Effect on abundance", main = "30 vs 120/480",
            cex.axis = 1, cex.main = 1, font = c(3,3,3,1))


```



## Second Survey (40 day)

```{r, warning=FALSE}
SS2_predictors <- data.frame(ID = ID_SS2_3_4,
                             treatments = treatments_SS2_3_4,
                             isolation = isolation_SS2_3_4,
                             isolation30_120480 = isolation30_120480_SS2_3_4,
                             isolation30120_480 = isolation30120_480_SS2_3_4,
                             treatments_contpast_sug = treatments_SS2_3_4_contpast_sug,
                             treatments_cont_pastsug = treatments_SS2_3_4_cont_pastsug,
                             treatments_contsug_past = treatments_SS2_3_4_contsug_past)
```


Number of latent variables:
```{r, cache = FALSE, warning=FALSE}
n_latent_tab_SS2 <- run_multiple_lv(num.lv = c(0,1,2,3),
                                    formula = ~ treatments * isolation,
                                    row.eff = ~ (1|ID),
                                    y = com_herb_det_SS2, X = SS2_predictors,
                                    family = "negative.binomial",
                                    method = "VA",
                                    n.init = 10, seed = 1:10)

n_latent_tab_SS2$AICc_tab

```
It looks that zero latent variables is the way to go.


Model selection of effects:
```{r, cache = FALSE, warning=FALSE}
model_herb_det_selection_SS2 <- run_multiple_gllvm(formulas = list(~ treatments,
                                                                    ~ isolation,
                                                                    ~ treatments + isolation,
                                                                    ~ treatments * isolation),
                                                    names = c("Treatments",
                                                              "Isolation",
                                                              "Isolation + Treatments",
                                                              "Isolation * Treatments"),
                                                    no_effect = TRUE,
                                                    num.lv = 0,
                                                    X = SS2_predictors,
                                                    X_row = data.frame(ID = ID_SS2_3_4),
                                                    y = com_herb_det_SS2,
                                                    row.eff = ~ (1|ID),
                                                    family = "negative.binomial",
                                                    method = "VA",
                                                    n.init = 10, seed = 1:10)

model_herb_det_selection_SS2$AICc_tab
```
It seems there are main effects of treatments and isolation.

Lets look at pairwise differences for treatments:
```{r, cache = FALSE, warning=FALSE}
model_herb_det_selection_SS2_post_hoc_treatments <- run_multiple_gllvm(formulas = list(~ treatments + isolation,
                                                                                        ~ treatments_contpast_sug + isolation,
                                                                                        ~ treatments_cont_pastsug + isolation,
                                                                                        ~ treatments_contsug_past + isolation),
                                                                        names = c("control # pasture # sugarcane",
                                                                                  "(control = pasture) # sugarcane",
                                                                                  "control # (pasture = sugarcane)",
                                                                                  "(control = sugarcane) # pasture"),
                                                                        no_effect = FALSE,
                                                                        num.lv = 0,
                                                                        X = SS2_predictors,
                                                                        X_row = data.frame(ID = ID_SS2_3_4),
                                                                        y = com_herb_det_SS2,
                                                                        row.eff = ~ (1|ID),
                                                                        family = "negative.binomial",
                                                                        method = "VA",
                                                                        n.init = 10, seed = 1:10)
model_herb_det_selection_SS2_post_hoc_treatments$AICc_tab
```
So, communities in the sugarcane treatment are different from the others.

Now isolation:
```{r, cache = FALSE, warning=FALSE}
model_herb_det_selection_SS2_post_hoc_isolation <- run_multiple_gllvm(formulas = list(~ isolation + treatments_cont_pastsug,
                                                                                      ~ isolation30120_480 + treatments_cont_pastsug,
                                                                                      ~ isolation30_120480 + treatments_cont_pastsug),
                                                                      names = c("30 # 120 # 480",
                                                                                "(30 = 120) # 480",
                                                                                "30 # (120 = 480)"),
                                                                      no_effect = FALSE,
                                                                      num.lv = 0,
                                                                      X = SS2_predictors,
                                                                      X_row = data.frame(ID = ID_SS2_3_4),
                                                                      y = com_herb_det_SS2,
                                                                      row.eff = ~ (1|ID),
                                                                      family = "negative.binomial",
                                                                      method = "VA",
                                                                      n.init = 10, seed = 1:10)
model_herb_det_selection_SS2_post_hoc_isolation$AICc_tab
```
All levels of isolation are different.



Ploting it:

```{r, dpi=150, fig.width=9, fig.height=6, fig.align = 'center', warning=FALSE}
SS2_predictors <- data.frame(treatments = treatments_SS1,
                             isolation = isolation_SS1)

sum_com_herb_det_SS2 <- sum_com_SS2[,Trait_SS2_sum$trophic == "consumer"]

col_SS2 <- rep("darkolivegreen3", ncol(sum_com_herb_det_SS2))
col_SS2[Trait_SS2_sum$trait[Trait_SS2_sum$trophic == "consumer"] == "insect_consumer" ] <- "cyan3"

fit_SS2_plot <- gllvm(sum_com_herb_det_SS2,
                      formula = ~ 1,
                      family = "negative.binomial",
                      method = "VA",
                      n.init = 10, num.lv = 2, seed = 11:20)


scaled_lvs <- get_scaled_lvs(fit_SS2_plot, alpha = 0.5)

set.seed(2)
scaled_lvs$species <- jitter(scaled_lvs$species, amount = 0.01)
set.seed(2)
scaled_lvs$sites <- jitter(scaled_lvs$sites, amount = 0.01)

scaled_lvs$new_species <- scaled_lvs$species/3


xmin <- min(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
xmax <- max(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
ymin <- min(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1
ymax <- max(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1


par(mar = c(4,4,1.25,.1), mfrow = c(2, 3))

plot_com_SS2_herb_treat_30()

plot_com_SS2_herb_treat_120()

plot_com_SS2_herb_treat_480()

par(mar = c(0,0,0,0),cex = 1.25)
plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(23, 23, 23), legend = c("Centroid - Control", "Centroid - Pasture", "Centroid - Sugarcane"), pt.bg	= c(col_control_30, col_pasture_30, col_sugarcane_30), bty = "n")

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21, 21, 21), legend = c("Ponds - Control", "Ponds - Pasture", "Ponds - Sugarcane"), pt.bg	= c(col_control_30, col_pasture_30, col_sugarcane_30), bty = "n", pt.cex	= 0.75)

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21, 21), legend = c("Insects", "Amphibians"), pt.bg	= c("cyan3","darkolivegreen3"), bty = "n", pt.cex	= 2.5, pt.lwd	= 1.5)

```


Now the coefficients for the effects observed.
```{r, dpi=150, fig.width=6, fig.height=3, fig.align = 'center', warning=FALSE}

species_labels_SS2 <- sub(pattern = ".", replacement = " ", x =names(effect_SS2_30_120), fixed = TRUE)
species_labels_SS2 <- sub(pattern = "Physalaemos", replacement = "P.", x =species_labels_SS2, fixed = TRUE)

par(mar = c(4,8,2,.5), cex = 0.5, mfrow = c(1,3))


My_coefplot(mles = effect_SS2_control_sugar_cane,
            lower = effect_SS2_control_sugar_cane_lower,
            upper = effect_SS2_control_sugar_cane_upper,
            species_labels = species_labels_SS2,  xlab = "Effect on abundance", main = "Sav./Past. vs Sug.",
            cex.axis = 1, cex.main = 1, font = c(1,1,3,3,3,3,3))#, at.xaxis = c(0, -10, -20, -30, -40, -50),break.axis = c(-25,-38))


```




```{r, dpi=150, fig.width=9, fig.height=6, fig.align = 'center', warning=FALSE}
par(mar = c(4,4,1.25,.1), mfrow = c(2, 3))

plot_com_SS2_herb_iso_control()

plot_com_SS2_herb_iso_pasture()

plot_com_SS2_herb_iso_sugarcane()

par(mar = c(0,0,0,0),cex = 1.25)
plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(22, 21, 24), legend = c("Centroid - 30 m", "Centroid - 120 m", "Centroid - 480 m"), pt.bg	= c(col_control_30, col_control_120, col_control_480), bty = "n")

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(15, 16, 17), legend = c("Ponds - 30 m", "Ponds - 120 m", "Ponds - 480 m"), col	= c(col_control_30, col_control_120, col_control_480), bty = "n", pt.cex	= 0.75)

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21, 21), legend = c("Insects", "Amphibians"), pt.bg	= c("cyan3","darkolivegreen3"), bty = "n", pt.cex	= 2.5, pt.lwd	= 1.5)

```


Now the coefficients for the effects observed.
```{r, dpi=150, fig.width=6, fig.height=3, fig.align = 'center', warning=FALSE}

species_labels_SS2 <- sub(pattern = ".", replacement = " ", x =names(effect_SS2_30_120), fixed = TRUE)
species_labels_SS2 <- sub(pattern = "Physalaemos", replacement = "P.", x =species_labels_SS2, fixed = TRUE)

par(mar = c(4,8,2,.5), mfrow = c(1,3), cex = 0.5)


My_coefplot(effect_SS2_30_120,
            effect_SS2_30_120_lower,
            effect_SS2_30_120_upper,
            species_labels = species_labels_SS2,  xlab = "Effect on abundance", main = "30 vs 120",
            cex.axis = 1, cex.main = 1, font = c(3,3,3,1,1,3,3,3,1))


My_coefplot(effect_SS2_120_480,
            effect_SS2_120_480_lower,
            effect_SS2_120_480_upper,
            species_labels = species_labels_SS2,  xlab = "Effect on abundance", main = "120 vs 480",
            cex.axis = 1, cex.main = 1, font = c(3,3,3,1,1,3,3,3,1))


My_coefplot(effect_SS2_30_480,
            effect_SS2_30_480_lower,
            effect_SS2_30_480_upper,
            species_labels = species_labels_SS2,  xlab = "Effect on abundance", main = "30 vs 480",
            cex.axis = 1, cex.main = 1, font = c(3,3,3,1,1,3,3,3,1))





```



## Third Survey (80 day)


```{r, warning=FALSE}
SS3_predictors <- data.frame(ID = ID_SS2_3_4,
                             treatments = treatments_SS2_3_4,
                             isolation = isolation_SS2_3_4,
                             isolation30_120480 = isolation30_120480_SS2_3_4,
                             isolation30120_480 = isolation30120_480_SS2_3_4,
                             treatments_contpast_sug = treatments_SS2_3_4_contpast_sug,
                             treatments_cont_pastsug = treatments_SS2_3_4_cont_pastsug,
                             treatments_contsug_past = treatments_SS2_3_4_contsug_past)
```


Number of latent variables:
```{r, cache = TRUE, warning=FALSE}
n_latent_tab_SS3 <- run_multiple_lv(num.lv = c(0,1,2,3),
                                    formula = ~ treatments * isolation,
                                    row.eff = ~ (1|ID),
                                    y = com_herb_det_SS3, X = SS3_predictors,
                                    family = "negative.binomial",
                                    method = "VA",
                                    n.init = 10, seed = 1:10)

n_latent_tab_SS3$AICc_tab

```
It looks that zero latent variables is the way to go.


Model selection of effects:
```{r, cache = TRUE, warning=FALSE}
model_herb_det_selection_SS3 <- run_multiple_gllvm(formulas = list(~ treatments,
                                                                    ~ isolation,
                                                                    ~ treatments + isolation,
                                                                    ~ treatments * isolation),
                                                    names = c("Treatments",
                                                              "Isolation",
                                                              "Isolation + Treatments",
                                                              "Isolation * Treatments"),
                                                    no_effect = TRUE,
                                                    num.lv = 0,
                                                    X = SS3_predictors,
                                                    X_row = data.frame(ID = ID_SS2_3_4),
                                                    y = com_herb_det_SS3,
                                                    row.eff = ~ (1|ID),
                                                    family = "negative.binomial",
                                                    method = "VA",
                                                    n.init = 10, seed = 1:10)

model_herb_det_selection_SS3$AICc_tab
```
It seems like there are interactive effects between isolation and agrochemical treatments.

Now we look for differences between agrochemical treatments in each isolation distance:
```{r, cache = TRUE, warning=FALSE}


#Treatments 30m
model_herb_det_selection_SS3_post_hoc_treatments_30 <- run_multiple_gllvm(formulas = list(~ treatments,
                                                                                       ~ treatments_contpast_sug,
                                                                                       ~ treatments_cont_pastsug,
                                                                                       ~ treatments_contsug_past),
                                                                       names = c("control # pasture # sugarcane",
                                                                                 "(control = pasture) # sugarcane",
                                                                                 "control # (pasture = sugarcane)",
                                                                                 "(control = sugarcane) # pasture"),
                                                                       no_effect = TRUE,
                                                                       num.lv = 0,
                                                                       X = SS3_predictors[isolation_SS2_3_4 == "30",],
                                                                       X_row = data.frame(ID = ID_SS2_3_4[isolation_SS2_3_4 == "30"]),
                                                                       y = com_herb_det_SS3[isolation_SS2_3_4 == "30",],
                                                                       row.eff = ~ (1|ID),
                                                                       family = "negative.binomial",
                                                                       method = "VA",
                                                                       n.init = 10, seed = 1:10, control = list(reltol = 1e-10, TMB = TRUE, optimizer = "optim", max.iter = 2000,
                                                                                                                 maxit = 4000, trace = FALSE, optim.method = "L-BFGS-B"))


model_herb_det_selection_SS3_post_hoc_treatments_30$AICc_tab



#Treatments 120m
model_herb_det_selection_SS3_post_hoc_treatments_120 <- run_multiple_gllvm(formulas = list(~ treatments,
                                                                                          ~ treatments_contpast_sug,
                                                                                          ~ treatments_cont_pastsug,
                                                                                          ~ treatments_contsug_past),
                                                                          names = c("control # pasture # sugarcane",
                                                                                    "(control = pasture) # sugarcane",
                                                                                    "control # (pasture = sugarcane)",
                                                                                    "(control = sugarcane) # pasture"),
                                                                          no_effect = TRUE,
                                                                          num.lv = 0,
                                                                          X = SS3_predictors[isolation_SS2_3_4 == "120",],
                                                                          X_row = data.frame(ID = ID_SS2_3_4[isolation_SS2_3_4 == "120"]),
                                                                          y = com_herb_det_SS3[isolation_SS2_3_4 == "120",],
                                                                          row.eff = ~ (1|ID),
                                                                          family = "negative.binomial",
                                                                          method = "VA",
                                                                          n.init = 10, seed = 1:10, control = list(reltol = 1e-10, TMB = TRUE, optimizer = "optim", max.iter = 2000,
                                                                                                                    maxit = 4000, trace = FALSE, optim.method = "L-BFGS-B"))

model_herb_det_selection_SS3_post_hoc_treatments_120$AICc_tab



#Treatments 480m
model_herb_det_selection_SS3_post_hoc_treatments_480 <- run_multiple_gllvm(formulas = list(~ treatments,
                                                                                           ~ treatments_contpast_sug,
                                                                                           ~ treatments_cont_pastsug,
                                                                                           ~ treatments_contsug_past),
                                                                           names = c("control # pasture # sugarcane",
                                                                                     "(control = pasture) # sugarcane",
                                                                                     "control # (pasture = sugarcane)",
                                                                                     "(control = sugarcane) # pasture"),
                                                                           no_effect = TRUE,
                                                                           num.lv = 0,
                                                                           X = SS3_predictors[isolation_SS2_3_4 == "480",],
                                                                           X_row = data.frame(ID = ID_SS2_3_4[isolation_SS2_3_4 == "480"]),
                                                                           y = com_herb_det_SS3[isolation_SS2_3_4 == "480",],
                                                                           row.eff = ~ (1|ID),
                                                                           family = "negative.binomial",
                                                                           method = "VA",
                                                                           n.init = 10, seed = 1:10, control = list(reltol = 1e-10, TMB = TRUE, optimizer = "optim", max.iter = 2000,
                                                                                                                     maxit = 4000, trace = FALSE, optim.method = "L-BFGS-B"))

model_herb_det_selection_SS3_post_hoc_treatments_480$AICc_tab

```
In all cases, sugarcane ponds were different from control and pasture, but probably in different ways. It will be important to look at plots of species coefficients to assess these differences. 


Now we look for differences between different isolation treatments in each agrochemical treatment:
```{r, warning=FALSE, cache = TRUE}
#Isolation controle
model_herb_det_selection_SS3_post_hoc_isolation_control <- run_multiple_gllvm(formulas = list(~ isolation,
                                                                                          ~ isolation30_120480,
                                                                                          ~ isolation30120_480),
                                                                          names = c("30 # 120 # 480",
                                                                                    "30 # (120 = 480)",
                                                                                    "(30 = 120) # 480"),
                                                                          no_effect = TRUE,
                                                                          num.lv = 0,
                                                                          X = SS3_predictors[treatments_SS2_3_4 == "control",],
                                                                          X_row = data.frame(ID = ID_SS2_3_4[treatments_SS2_3_4 == "control"]),
                                                                          y = com_herb_det_SS3[treatments_SS2_3_4 == "control",],
                                                                          row.eff = ~ (1|ID),
                                                                          family = "negative.binomial",
                                                                          method = "VA",
                                                                          n.init = 10, seed = 1:10, control = list(reltol = 1e-10, TMB = TRUE, optimizer = "optim", max.iter = 2000,
                                                                                                                    maxit = 4000, trace = FALSE, optim.method = "L-BFGS-B"))

model_herb_det_selection_SS3_post_hoc_isolation_control$AICc_tab




#Isolation pasture
model_herb_det_selection_SS3_post_hoc_isolation_pasture <- run_multiple_gllvm(formulas = list(~ isolation,
                                                                                              ~ isolation30_120480,
                                                                                              ~ isolation30120_480),
                                                                              names = c("30 # 120 # 480",
                                                                                        "30 # (120 = 480)",
                                                                                        "(30 = 120) # 480"),
                                                                              no_effect = TRUE,
                                                                              num.lv = 0,
                                                                              X = SS3_predictors[treatments_SS2_3_4 == "pasture",],
                                                                              X_row = data.frame(ID = ID_SS2_3_4[treatments_SS2_3_4 == "pasture"]),
                                                                              y = com_herb_det_SS3[treatments_SS2_3_4 == "pasture",],
                                                                              row.eff = ~ (1|ID),
                                                                              family = "negative.binomial",
                                                                              method = "VA",
                                                                              n.init = 10, seed = 1:10, pasture = list(reltol = 1e-10, TMB = TRUE, optimizer = "optim", max.iter = 2000,
                                                                                                                        maxit = 4000, trace = FALSE, optim.method = "L-BFGS-B"))

model_herb_det_selection_SS3_post_hoc_isolation_pasture$AICc_tab



#Isolation sugarcane
model_herb_det_selection_SS3_post_hoc_isolation_sugarcane <- run_multiple_gllvm(formulas = list(~ isolation,
                                                                                              ~ isolation30_120480,
                                                                                              ~ isolation30120_480),
                                                                              names = c("30 # 120 # 480",
                                                                                        "30 # (120 = 480)",
                                                                                        "(30 = 120) # 480"),
                                                                              no_effect = TRUE,
                                                                              num.lv = 0,
                                                                              X = SS3_predictors[treatments_SS2_3_4 == "sugar_cane",],
                                                                              X_row = data.frame(ID = ID_SS2_3_4[treatments_SS2_3_4 == "sugar_cane"]),
                                                                              y = com_herb_det_SS3[treatments_SS2_3_4 == "sugar_cane",],
                                                                              row.eff = ~ (1|ID),
                                                                              family = "negative.binomial",
                                                                              method = "VA",
                                                                              n.init = 10, seed = 1:10, sugarcane = list(reltol = 1e-10, TMB = TRUE, optimizer = "optim", max.iter = 2000,
                                                                                                                        maxit = 4000, trace = FALSE, optim.method = "L-BFGS-B"))

model_herb_det_selection_SS3_post_hoc_isolation_sugarcane$AICc_tab

```
For control ponds, 480m is different from the 30 and 120m.
For pasture ponds, all levels of isolation are different.
For sugarcane ponds, 480m is different from the 30 and 120m. 



Ploting it:

```{r, dpi=150, fig.width=9, fig.height=6, fig.align = 'center', warning=FALSE}
SS3_predictors <- data.frame(treatments = treatments_SS1,
                             isolation = isolation_SS1)

sum_com_herb_det_SS3 <- sum_com_SS3[,Trait_SS3_sum$trophic == "consumer"]

col_SS3 <- rep("darkolivegreen3", ncol(sum_com_herb_det_SS3))
col_SS3[Trait_SS3_sum$trait[Trait_SS3_sum$trophic == "consumer"] == "insect_consumer" ] <- "cyan3"





fit_SS3_plot <- gllvm(sum_com_herb_det_SS3,
                      formula = ~ 1,
                      family = "negative.binomial",
                      method = "VA",
                      n.init = 10, num.lv = 2, seed = 11:20)


scaled_lvs <- get_scaled_lvs(fit_SS3_plot, alpha = 0.5)

scaled_lvs$new_species <- scaled_lvs$species/3

xmin <- min(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
xmax <- max(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
ymin <- min(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1
ymax <- max(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1


par(mar = c(4,4,1.25,.1), mfrow = c(2, 3))

plot_com_SS3_herb_treat_30()

plot_com_SS3_herb_treat_120()

plot_com_SS3_herb_treat_480()

par(mar = c(0,0,0,0),cex = 1.25)
plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(23, 23, 23), legend = c("Centroid - Control", "Centroid - Pasture", "Centroid - Sugarcane"), pt.bg	= c(col_control_30, col_pasture_30, col_sugarcane_30), bty = "n")

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21, 21, 21), legend = c("Ponds - Control", "Ponds - Pasture", "Ponds - Sugarcane"), pt.bg	= c(col_control_30, col_pasture_30, col_sugarcane_30), bty = "n", pt.cex	= 0.75)

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21, 21), legend = c("Insects", "Amphibians"), pt.bg	= c("cyan3","darkolivegreen3"), bty = "n", pt.cex	= 2.5, pt.lwd	= 1.5)



```

Now coefficients
```{r, dpi=150, fig.width=6, fig.height=3, fig.align = 'center', warning=FALSE}
species_labels_SS3 <- sub(pattern = ".", replacement = " ", x =names(effect_SS3_30_120_480_control), fixed = TRUE)
species_labels_SS3 <- sub(pattern = "Physalaemos", replacement = "P.", x =species_labels_SS3, fixed = TRUE)


par(mar = c(4,8,2,.5), mfrow = c(1,3), cex = 0.5)


My_coefplot(mles = effect_SS3_30_control_sugar_cane,
            lower = effect_SS3_30_control_sugar_cane_lower,
            upper = effect_SS3_30_control_sugar_cane_upper,
            species_labels = species_labels_SS3,  xlab = "Effect on abundance", main = "Sav./Past. vs Sug. (30 m)",
            cex.axis = 1, cex.main = 1, font = c(1,3,3,1,3,3,3,3,1,3), at.xaxis = c(10,0,-10, -20,-30, -40, -130),break.axis = c(-40,-120))


My_coefplot(mles = effect_SS3_120_control_sugar_cane,
            lower = effect_SS3_120_control_sugar_cane_lower,
            upper = effect_SS3_120_control_sugar_cane_upper,
            species_labels = species_labels_SS3,  xlab = "Effect on abundance", main = "Sav./Past. vs Sug. (120 m)",
            cex.axis = 1, cex.main = 1, font = c(1,3,3,1,3,3,3,3,1,3), at.xaxis = c(0,-7, -14,-21, -28))


My_coefplot(mles = effect_SS3_480_control_sugar_cane,
            lower = effect_SS3_480_control_sugar_cane_lower,
            upper = effect_SS3_480_control_sugar_cane_upper,
            species_labels = species_labels_SS3,  xlab = "Effect on abundance", main = "Sav./Past. vs Sug. (480 m)",
            cex.axis = 1, cex.main = 1, font = c(1,3,3,1,3,3,3,3,1,3))#, at.xaxis = c(10,0,-10, -20,-30, -40, -130),break.axis = c(-40,-480))


```



```{r, dpi=150, fig.width=9, fig.height=6, fig.align = 'center', warning=FALSE}

par(mar = c(4,4,1.25,.1), mfrow = c(2, 3))

plot_com_SS3_herb_iso_control()

plot_com_SS3_herb_iso_pasture()

plot_com_SS3_herb_iso_sugarcane()

par(mar = c(0,0,0,0),cex = 1.25)
plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(22, 21, 24), legend = c("Centroid - 30 m", "Centroid - 120 m", "Centroid - 480 m"), pt.bg	= c(col_control_30, col_control_120, col_control_480), bty = "n")

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(15, 16, 17), legend = c("Ponds - 30 m", "Ponds - 120 m", "Ponds - 480 m"), col	= c(col_control_30, col_control_120, col_control_480), bty = "n", pt.cex	= 0.75)

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21, 21), legend = c("Insects", "Amphibians"), pt.bg	= c("cyan3","darkolivegreen3"), bty = "n", pt.cex	= 2.5, pt.lwd	= 1.5)

```


Now coefficients
```{r, dpi=150, fig.width=6, fig.height=3, fig.align = 'center', warning=FALSE}

par(mar = c(4,8,2,.5), mfrow = c(1,3), cex = 0.5)

#Control
My_coefplot(mles = effect_SS3_30_120_480_control,
            lower = effect_SS3_30_120_480_control_lower,
            upper = effect_SS3_30_120_480_control_upper,
            species_labels = species_labels_SS3,  xlab = "Effect on abundance", main = "30/120 vs 480 (Control)",
            cex.axis = 1, cex.main = 1, font = c(1,3,3,1,3,3,3,3,1,3), at.xaxis = c(4, 2, 0, -2, -3, -4, -123),
            break.axis = c(-3,-122))


par(mar = c(4,8,2,.5), mfrow = c(1,3), cex = 0.5)
#Pasture
My_coefplot(mles = effect_SS3_pasture_30_120,
            lower = effect_SS3_pasture_30_120_lower,
            upper = effect_SS3_pasture_30_120_upper,
            species_labels = species_labels_SS3,  xlab = "Effect on abundance", main = "30 vs 120 (Pasture)",
            cex.axis = 1, cex.main = 1, font = c(1,3,3,1,3,3,3,3,1,3), at.xaxis = c(0, -50, -100, -150, -200, -400, -450),
            break.axis = c(-130,-390))


My_coefplot(mles = effect_SS3_pasture_30_480,
            lower = effect_SS3_pasture_30_480_lower,
            upper = effect_SS3_pasture_30_480_upper,
            species_labels = species_labels_SS3,  xlab = "Effect on abundance", main = "30 vs 480 (Pasture)",
            cex.axis = 1, cex.main = 1, font = c(1,3,3,1,3,3,3,3,1,3), at.xaxis = c(4,2,0,-2,-4,-6, -516),
            break.axis = c(-5,-514))


My_coefplot(mles = effect_SS3_pasture_120_480,
            lower = effect_SS3_pasture_120_480_lower,
            upper = effect_SS3_pasture_120_480_upper,
            species_labels = species_labels_SS3,  xlab = "Effect on abundance", main = "120 vs 480 (Pasture)",
            cex.axis = 1, cex.main = 1, font = c(1,3,3,1,3,3,3,3,1,3))#, at.xaxis = c(4,2,0,-2,-4,-6, -516), break.axis = c(-5,-514))


#Sugarcane
par(mar = c(4,8,2,.5), mfrow = c(1,3), cex = 0.5)

My_coefplot(mles = effect_SS3_30_120_480_sugar_cane,
            lower = effect_SS3_30_120_480_sugar_cane_lower,
            upper = effect_SS3_30_120_480_sugar_cane_upper,
            species_labels = species_labels_SS3,  xlab = "Effect on abundance", main = "30/120 vs 480 (Sugarcane)",
            cex.axis = 1, cex.main = 1, font = c(1,3,3,1,3,3,3,3,1,3), at.xaxis = c(0, -10, -20, -30, -40, -50),break.axis = c(-25,-38))



```



## Fourth Survey (160 day)

```{r, warning=FALSE}
SS4_predictors <- data.frame(ID = as.character(ID_SS2_3_4),
                             treatments = treatments_SS2_3_4,
                             isolation = isolation_SS2_3_4,
                             isolation30_120480 = isolation30_120480_SS2_3_4,
                             isolation30120_480 = isolation30120_480_SS2_3_4,
                             treatments_contpast_sug = treatments_SS2_3_4_contpast_sug,
                             treatments_cont_pastsug = treatments_SS2_3_4_cont_pastsug,
                             treatments_contsug_past = treatments_SS2_3_4_contsug_past)
```


Number of latent variables:
```{r, cache = TRUE, warning=FALSE}
n_latent_tab_SS4 <- run_multiple_lv(num.lv = c(0,1,2,3),
                                    formula = ~ treatments * isolation,
                                    row.eff = ~ (1|ID),
                                    y = com_herb_det_SS4, X = SS4_predictors,
                                    family = "negative.binomial",
                                    method = "VA",
                                    n.init = 10, seed = 1:10)

n_latent_tab_SS4$AICc_tab

```
It looks that zero latent variables is the way to go.


Model selection of effects:
```{r, cache = TRUE, warning=FALSE}
model_herb_det_selection_SS4 <- run_multiple_gllvm(formulas = list(~ treatments,
                                                                   ~ isolation,
                                                                   ~ treatments + isolation,
                                                                   ~ treatments * isolation),
                                                   names = c("Treatments",
                                                             "Isolation",
                                                             "Isolation + Treatments",
                                                             "Isolation * Treatments"),
                                                   no_effect = TRUE,
                                                   num.lv = 0,
                                                   X = SS4_predictors,
                                                   X_row = data.frame(ID = ID_SS2_3_4),
                                                   y = com_herb_det_SS4,
                                                   row.eff = ~ (1|ID),
                                                   family = "negative.binomial",
                                                   method = "VA",
                                                   n.init = 10, seed = 1:10)

model_herb_det_selection_SS4$AICc_tab
```
Ok. Here the model that includes the interaction between isolation is the most plausible model (dAIC = 0). But the one that includes only main effects is considered similarly plausible by the rule of thumb of dAIC > 2. Technically,  It seems like the model that includes the interaction is about 6.5 times more plausible (exponential of 1.88) than the one that does not. Therefore here we will consider the model that includes the interaction the most plausible model.




Now we look for differences between agrochemical treatments in each isolation distance:
```{r, cache = TRUE, warning=FALSE}
#Treatments 30m
model_herb_det_selection_SS4_post_hoc_treatments_30 <- run_multiple_gllvm(formulas = list(~ treatments,
                                                                                          ~ treatments_contpast_sug,
                                                                                          ~ treatments_cont_pastsug,
                                                                                          ~ treatments_contsug_past),
                                                                          names = c("control # pasture # sugarcane",
                                                                                    "(control = pasture) # sugarcane",
                                                                                    "control # (pasture = sugarcane)",
                                                                                    "(control = sugarcane) # pasture"),
                                                                          no_effect = TRUE,
                                                                          num.lv = 0,
                                                                          X = SS4_predictors[isolation_SS2_3_4 == "30",],
                                                                          X_row = data.frame(ID = ID_SS2_3_4[isolation_SS2_3_4 == "30"]),
                                                                          y = com_herb_det_SS4[isolation_SS2_3_4 == "30",],
                                                                          row.eff = ~ (1|ID),
                                                                          family = "negative.binomial",
                                                                          method = "VA",
                                                                          n.init = 10, seed = 1:10, control = list(reltol = 1e-10, TMB = TRUE, optimizer = "optim", max.iter = 2000,
                                                                                                                    maxit = 4000, trace = FALSE, optim.method = "L-BFGS-B"))

model_herb_det_selection_SS4_post_hoc_treatments_30$AICc_tab



#Treatments 120m
model_herb_det_selection_SS4_post_hoc_treatments_120 <- run_multiple_gllvm(formulas = list(~ treatments,
                                                                                           ~ treatments_contpast_sug,
                                                                                           ~ treatments_cont_pastsug,
                                                                                           ~ treatments_contsug_past),
                                                                           names = c("control # pasture # sugarcane",
                                                                                     "(control = pasture) # sugarcane",
                                                                                     "control # (pasture = sugarcane)",
                                                                                     "(control = sugarcane) # pasture"),
                                                                           no_effect = TRUE,
                                                                           num.lv = 0,
                                                                           X = SS4_predictors[isolation_SS2_3_4 == "120",],
                                                                           X_row = data.frame(ID = ID_SS2_3_4[isolation_SS2_3_4 == "120"]),
                                                                           y = com_herb_det_SS4[isolation_SS2_3_4 == "120",],
                                                                           row.eff = ~ (1|ID),
                                                                           family = "negative.binomial",
                                                                           method = "VA",
                                                                           n.init = 10, seed = 1:10, control = list(reltol = 1e-10, TMB = TRUE, optimizer = "optim", max.iter = 2000,
                                                                                                                     maxit = 4000, trace = FALSE, optim.method = "L-BFGS-B"))

model_herb_det_selection_SS4_post_hoc_treatments_120$AICc_tab


#Treatments 480m
model_herb_det_selection_SS4_post_hoc_treatments_480 <- run_multiple_gllvm(formulas = list(~ treatments,
                                                                                           ~ treatments_contpast_sug,
                                                                                           ~ treatments_cont_pastsug,
                                                                                           ~ treatments_contsug_past),
                                                                           names = c("control # pasture # sugarcane",
                                                                                     "(control = pasture) # sugarcane",
                                                                                     "control # (pasture = sugarcane)",
                                                                                     "(control = sugarcane) # pasture"),
                                                                           no_effect = TRUE,
                                                                           num.lv = 0,
                                                                           X = SS4_predictors[isolation_SS2_3_4 == "480",],
                                                                           X_row = data.frame(ID = ID_SS2_3_4[isolation_SS2_3_4 == "480"]),
                                                                           y = com_herb_det_SS4[isolation_SS2_3_4 == "480",],
                                                                           row.eff = ~ (1|ID),
                                                                           family = "negative.binomial",
                                                                           method = "VA",
                                                                           n.init = 10, seed = 1:10, control = list(reltol = 1e-10, TMB = TRUE, optimizer = "optim", max.iter = 2000,
                                                                                                                     maxit = 4000, trace = FALSE, optim.method = "L-BFGS-B"))

model_herb_det_selection_SS4_post_hoc_treatments_480$AICc_tab




```
In 30m. All treatments are different
In 120m. Sugarcane is different from the others
In 480m. There is no difference among treatments.


Now we look for differences between different isolation treatments in each agrochemical treatment:
```{r, warning=FALSE, cache = TRUE}
#Isolation controle
#Isolation controle
model_herb_det_selection_SS4_post_hoc_isolation_control <- run_multiple_gllvm(formulas = list(~ isolation,
                                                                                              ~ isolation30_120480,
                                                                                              ~ isolation30120_480),
                                                                              names = c("30 # 120 # 480",
                                                                                        "30 # (120 = 480)",
                                                                                        "(30 = 120) # 480"),
                                                                              no_effect = TRUE,
                                                                              num.lv = 0,
                                                                              X = SS4_predictors[treatments_SS2_3_4 == "control",],
                                                                              X_row = data.frame(ID = ID_SS2_3_4[treatments_SS2_3_4 == "control"]),
                                                                              y = com_herb_det_SS4[treatments_SS2_3_4 == "control",],
                                                                              row.eff = ~ (1|ID),
                                                                              family = "negative.binomial",
                                                                              method = "VA",
                                                                              n.init = 10, seed = 1:10, control = list(reltol = 1e-10, TMB = TRUE, optimizer = "optim", max.iter = 2000,
                                                                                                                        maxit = 4000, trace = FALSE, optim.method = "L-BFGS-B"))

model_herb_det_selection_SS4_post_hoc_isolation_control$AICc_tab




#Isolation pasture
model_herb_det_selection_SS4_post_hoc_isolation_pasture <- run_multiple_gllvm(formulas = list(~ isolation,
                                                                                              ~ isolation30_120480,
                                                                                              ~ isolation30120_480),
                                                                              names = c("30 # 120 # 480",
                                                                                        "30 # (120 = 480)",
                                                                                        "(30 = 120) # 480"),
                                                                              no_effect = TRUE,
                                                                              num.lv = 0,
                                                                              X = SS4_predictors[treatments_SS2_3_4 == "pasture",],
                                                                              X_row = data.frame(ID = ID_SS2_3_4[treatments_SS2_3_4 == "pasture"]),
                                                                              y = com_herb_det_SS4[treatments_SS2_3_4 == "pasture",],
                                                                              row.eff = ~ (1|ID),
                                                                              family = "negative.binomial",
                                                                              method = "VA",
                                                                              n.init = 10, seed = 1:10, pasture = list(reltol = 1e-10, TMB = TRUE, optimizer = "optim", max.iter = 2000,
                                                                                                                        maxit = 4000, trace = FALSE, optim.method = "L-BFGS-B"))

model_herb_det_selection_SS4_post_hoc_isolation_pasture$AICc_tab



#Isolation sugarcane
model_herb_det_selection_SS4_post_hoc_isolation_sugarcane <- run_multiple_gllvm(formulas = list(~ isolation,
                                                                                                ~ isolation30_120480,
                                                                                                ~ isolation30120_480),
                                                                                names = c("30 # 120 # 480",
                                                                                          "30 # (120 = 480)",
                                                                                          "(30 = 120) # 480"),
                                                                                no_effect = TRUE,
                                                                                num.lv = 0,
                                                                                X = SS4_predictors[treatments_SS2_3_4 == "sugar_cane",],
                                                                                X_row = data.frame(ID = ID_SS2_3_4[treatments_SS2_3_4 == "sugar_cane"]),
                                                                                y = com_herb_det_SS4[treatments_SS2_3_4 == "sugar_cane",],
                                                                                row.eff = ~ (1|ID),
                                                                                family = "negative.binomial",
                                                                                method = "VA",
                                                                                n.init = 10, seed = 1:10, sugarcane = list(reltol = 1e-10, TMB = TRUE, optimizer = "optim", max.iter = 2000,
                                                                                                                            maxit = 4000, trace = FALSE, optim.method = "L-BFGS-B"))

model_herb_det_selection_SS4_post_hoc_isolation_sugarcane$AICc_tab


```
For control ponds, 30m is different from 120 and 480m.
For pasture ponds, all levels of isolation are different.
For sugarcane ponds, 480m is different from the 30 and 120m. 



Ploting it:

```{r, dpi=150, fig.width=9, fig.height=6, fig.align = 'center', warning=FALSE}
SS4_predictors <- data.frame(treatments = treatments_SS1,
                             isolation = isolation_SS1,
                             treatments_contpast_sug = treatments_contpast_sug)

sum_com_herb_det_SS4 <- sum_com_SS4[,Trait_SS4_sum$trophic == "consumer"]

col_SS4 <- rep("darkolivegreen3", ncol(sum_com_herb_det_SS4))
col_SS4[Trait_SS4_sum$trait[Trait_SS4_sum$trophic == "consumer"] == "insect_consumer" ] <- "cyan3"


fit_SS4_plot <- gllvm(sum_com_herb_det_SS4,
                      formula = ~ 1,
                      family = "negative.binomial",
                      #row.eff = "random",
                      method = "VA",
                      n.init = 10, num.lv = 2, seed = 1:10)


scaled_lvs <- get_scaled_lvs(fit_SS4_plot, alpha = 0.5)


scaled_lvs$new_species <- scaled_lvs$species/3


xmin <- min(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
xmax <- max(c(scaled_lvs$sites[,1], scaled_lvs$new_species[,1]))*1.1
ymin <- min(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1
ymax <- max(c(scaled_lvs$sites[,2], scaled_lvs$new_species[,2]))*1.1

par(mar = c(4,4,1.25,.1), mfrow = c(2, 3))

plot_com_SS4_herb_treat_30()

plot_com_SS4_herb_treat_120()

plot_com_SS4_herb_treat_480()

par(mar = c(0,0,0,0),cex = 1.25)
plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(23, 23, 23), legend = c("Centroid - Control", "Centroid - Pasture", "Centroid - Sugarcane"), pt.bg	= c(col_control_30, col_pasture_30, col_sugarcane_30), bty = "n")

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21, 21, 21), legend = c("Ponds - Control", "Ponds - Pasture", "Ponds - Sugarcane"), pt.bg	= c(col_control_30, col_pasture_30, col_sugarcane_30), bty = "n", pt.cex	= 0.75)

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21, 21), legend = c("Insects", "Amphibians"), pt.bg	= c("cyan3","darkolivegreen3"), bty = "n", pt.cex	= 2.5, pt.lwd	= 1.5)


```


Plotting coefficients:
```{r, dpi=150, fig.width=6, fig.height=3, fig.align = 'center', warning=FALSE}
species_labels_SS4 <- sub(pattern = ".", replacement = " ", x =names(effect_SS4_30_120_480_control), fixed = TRUE)
species_labels_SS4 <- sub(pattern = "Physalaemos", replacement = "P.", x =species_labels_SS4, fixed = TRUE)

#30
par(mar = c(4,8,2,.5), mfrow = c(1,3), cex = 0.5)

My_coefplot(mles = effect_SS4_30_control_pasture,
            lower = effect_SS4_30_control_pasture_lower,
            upper = effect_SS4_30_control_pasture_upper,
            species_labels = species_labels_SS4,  xlab = "Effect on abundance", main = "Sav. vs Past. (30 m)",
            cex.axis = 1, cex.main = 1, font = c(1,1,3,3,3,3,3))#, at.xaxis = c(10,0,-10, -20,-30, -40, -130),break.axis = c(-40,-480))


My_coefplot(mles = effect_SS4_30_control_sugar_cane,
            lower = effect_SS4_30_control_sugar_cane_lower,
            upper = effect_SS4_30_control_sugar_cane_upper,
            species_labels = species_labels_SS4,  xlab = "Effect on abundance", main = "Sav. vs Sug. (30 m)",
            cex.axis = 1, cex.main = 1, font = c(1,1,3,3,3,3,3), at.xaxis = c(5,0,-5,-10, -510),break.axis = c(-10,-505))


My_coefplot(mles = effect_SS4_30_pasture_sugar_cane,
            lower = effect_SS4_30_pasture_sugar_cane_lower,
            upper = effect_SS4_30_pasture_sugar_cane_upper,
            species_labels = species_labels_SS4,  xlab = "Effect on abundance", main = "Pas. vs Sug. (30 m)",
            cex.axis = 1, cex.main = 1, font = c(1,1,3,3,3,3,3))#, at.xaxis = c(5,0,-5,-10, -510),break.axis = c(-10,-505))

#120
par(mar = c(4,8,2,.5), mfrow = c(1,3), cex = 0.5)

My_coefplot(mles = effect_SS4_120_control_sugar_cane,
            lower = effect_SS4_120_control_sugar_cane_lower,
            upper = effect_SS4_120_control_sugar_cane_upper,
            species_labels = species_labels_SS4,  xlab = "Effect on abundance", main = "Sav./Past. vs Sug. (120 m)",
            cex.axis = 1, cex.main = 1, font = c(1,1,3,3,3,3,3), at.xaxis = c(0,-7,-14, -21, - 28))



```



```{r, dpi=150, fig.width=9, fig.height=6, fig.align = 'center', warning=FALSE}

par(mar = c(4,4,1.25,.1), mfrow = c(2, 3))

plot_com_SS4_herb_iso_control()

plot_com_SS4_herb_iso_pasture()

plot_com_SS4_herb_iso_sugarcane()

par(mar = c(0,0,0,0),cex = 1.25)
plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(22, 21, 24), legend = c("Centroid - 30 m", "Centroid - 120 m", "Centroid - 480 m"), pt.bg	= c(col_control_30, col_control_120, col_control_480), bty = "n")

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(15, 16, 17), legend = c("Ponds - 30 m", "Ponds - 120 m", "Ponds - 480 m"), col	= c(col_control_30, col_control_120, col_control_480), bty = "n", pt.cex	= 0.75)

plot(NA, xaxt = "n", yaxt = "n", xlim= c(0,100), ylim = c(0,100), bty = "n", ylab = "", xlab = "")
legend(x = 0, y = 100, pch = c(21, 21), legend = c("Insects", "Amphibians"), pt.bg	= c("cyan3","darkolivegreen3"), bty = "n", pt.cex	= 2.5, pt.lwd	= 1.5)

```


Plotting coefficients:
```{r, dpi=150, fig.width=6, fig.height=3, fig.align = 'center', warning=FALSE}


#Control
par(mar = c(4,8,2,.5), mfrow = c(1,3), cex = 0.5)

My_coefplot(mles = effect_SS4_30_120_480_control,
            lower = effect_SS4_30_120_480_control_lower,
            upper = effect_SS4_30_120_480_control_upper,
            species_labels = species_labels_SS4,  xlab = "Effect on abundance", main = "30 vs 120/480 (Control)",
            cex.axis = 1, cex.main = 1, font = c(1,1,3,3,3,3,3))#, at.xaxis = c(4, 2, 0, -2, -3, -4, -123),
# break.axis = c(-3,-122))

#Pasture
par(mar = c(4,8,2,.5), mfrow = c(1,3), cex = 0.5)

My_coefplot(mles = effect_SS4_pasture_30_120,
            lower = effect_SS4_pasture_30_120_lower,
            upper = effect_SS4_pasture_30_120_upper,
            species_labels = species_labels_SS4,  xlab = "Effect on abundance", main = "30 vs 120 (Pasture)",
            cex.axis = 1, cex.main = 1, font = c(1,1,3,3,3,3,3), at.xaxis = c(6, 3, 0, -3, -6, -24, -27), break.axis = c(-7,-25))


My_coefplot(mles = effect_SS4_pasture_30_480,
            lower = effect_SS4_pasture_30_480_lower,
            upper = effect_SS4_pasture_30_480_upper,
            species_labels = species_labels_SS4,  xlab = "Effect on abundance", main = "30 vs 480 (Pasture)",
            cex.axis = 1, cex.main = 1, font = c(1,1,3,3,3,3,3))#, at.xaxis = c(4,2,0,-2,-4,-6, -516),  break.axis = c(-5,-514))


My_coefplot(mles = effect_SS4_pasture_120_480,
            lower = effect_SS4_pasture_120_480_lower,
            upper = effect_SS4_pasture_120_480_upper,
            species_labels = species_labels_SS4,  xlab = "Effect on abundance", main = "120 vs 480 (Pasture)",
            cex.axis = 1, cex.main = 1, font = c(1,1,3,3,3,3,3), at.xaxis = c(15,10,5,0,-5,-10, -150), break.axis = c(-10,-145))


#Sugarcane
par(mar = c(4,8,2,.5), mfrow = c(1,3), cex = 0.5)

My_coefplot(mles = effect_SS4_30_120_480_sugar_cane,
            lower = effect_SS4_30_120_480_sugar_cane_lower,
            upper = effect_SS4_30_120_480_sugar_cane_upper,
            species_labels = species_labels_SS4,  xlab = "Effect on abundance", main = "30 vs 120/480 (Sugarcane)",
            cex.axis = 1, cex.main = 1, font = c(1,1,3,3,3,3,3))#, at.xaxis = c(0, -10, -20, -30, -40, -50),break.axis = c(-25,-38))

```

